---
title: "India ILC - Manuscript Analysis"
author: "Jeremy Lowe"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, message = FALSE)

```


```{r package loading, include=FALSE}

#Package names
packages <- c("rsurveycto", "expss", "labelled", "httr", "lubridate", "quantitray",
              "sjmisc", "knitr", "kableExtra", "readxl", "experiment", "stargazer",
              "haven", "googlesheets4", "ggsignif", "patchwork", "table1", "gtsummary",
              "gt", "webshot2", "clubSandwich", "sandwich", "lmtest", "broom",
              "tidyverse", "sf", "gridExtra", "crosstable", "viridis", "flextable")

#Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

#Packages loading
invisible(lapply(packages, library, character.only = TRUE))



```



```{r profile}
#------------------------ setting user path ----------------------------------------#

# setting github directory
github_path <- function() {
  user <- Sys.info()["user"]
  if (user == "asthavohra") {
    github = "/Users/asthavohra/Documents/GitHub/i-h2o-india/Code/2_Pilot/0_pilot logistics/"
  } 
  else if (user=="akitokamei"){
    github = "/Users/akitokamei/Library/CloudStorage/Dropbox/Mac/Documents/GitHub/i-h2o-india/Code/2_Pilot/0_pilot logistics/"
  } 
  else if (user == "jerem") {
    github = "C:/Users/jerem/Documents/i-h2o-india/Code"
  } 
  else {
    warning("No path found for current user (", user, ")")
    github = getwd()
  }
  
  stopifnot(file.exists(github))
  return(github)
}

github <- github_path()



#Setting all other user paths

source(paste0(github_path(),"/3_manuscript/0-config.R"))



```


# Loading Data

```{r dataset loading}

#Loading different final datasets from Box
#See Process Doc for details on cleaning code and clean datasets:
#https://docs.google.com/document/d/1Hpv5HF5ICO5FSVdQnPtDECCYORn2qy5S7C_KIx0pDuM/edit


#from Box

#bl_raw <- read_csv(paste0(user_path(), "/1_raw/Baseline follow up survey_WIDE.csv"))

#Baseline Survey
bl <- read_stata(paste0(user_path(), "/3_final/1_2_FU_clean_final.dta"))

#Baseline Census
cen <- read_stata(paste0(user_path(),"/3_final/1_1_Baseline_Census_HH_clean_consented.dta"))

#Round 1 survey
r1 <- read_stata(paste0(user_path(),"/3_final/1_5_FU_R1_clean_final.dta"))

#Round 2 survey
r2 <- read_stata(paste0(user_path(),"/3_final/1_6_FU_R2_clean_final.dta"))

#Round 3 survey
r3 <- read_stata(paste0(user_path(),"/3_final/1_7_FU_R3_clean_final.dta"))

#Round 4 survey
r4 <- read_csv(paste0(user_path(),"/3_final/1_10_monthly_follow_up_cleaned.csv"))

#Round 5 survey
r5 <- read_csv(paste0(user_path(),"/3_final/1_10_monthly_follow_up_cleaned_R2.csv"))

#Round 6 survey
r6 <- read_csv(paste0(user_path(),"/3_final/1_10_monthly_follow_up_cleaned_R3.csv"))


#All rounds
r_all <- read_stata(paste0(user_path(),"/3_final/0_Master_HHLevel_FU_Census.dta"))

#Chlorine Monitoring Survey
mon <- read_stata(paste0(user_path(),"/3_final/1_X_chlorine_monitoring.dta"))

#Longitudinal Chlorine Monitoring
mon_long <- read_csv(paste0(user_path(),"/3_final/longitudinal_testing_cleaned.csv"))


#Longitudinal chlorine monitoring form
#mon_full <- read_csv("C:/Users/jerem/Box/India Water project/2_Pilot/Data/1_raw/india_ilc_pilot_monitoring_WIDE.csv")

gv <- read_csv(paste0(user_path(), "/6_Gram Vikas/India ILC - Gram Vikas Chlorine Monitoring_current.csv"))

#Baseline IDEXX
idexx <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/BL_idexx_master_cleaned.csv"))

#Baseline ABR IDEXX
#abr <- read_xlsx("C:/Users/jerem/Box/India Water project/2_Pilot/Data/5_lab data/idexx/raw/_India ILC_ABR_data_MASTER.xlsx", skip = 1)

#IDEXX Round 1
idexx_r1 <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/R1_idexx_master_cleaned.csv"))


#IDEXX Round 2
idexx_r2 <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/R2_idexx_master_cleaned.csv"))

#IDEXX Round 3
idexx_r3 <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/R3_idexx_master_cleaned.csv"))

#Pooled IDEXX Rounds
idexx_tab <- read_csv(paste0(user_path(),"/3_final/POOLED_idexx_master_cleaned.csv"))

#Pooled IDEXX Rounds
idexx_abr <- read_csv(paste0(user_path(),"/3_final/POOLED_idexx_ABR_master_cleaned.csv"))

#Checking Michelle's cleaned IDEXX data
idexx_mc <- read_stata(paste0(user_path(),"/2_deidentified/Ecoli results followup_cleaned_WIDE.dta"))

#Village Details
#village_details_old <- read_xlsx(paste0(user_path(),"/5_lab data/India_ILC_Pilot_Rayagada_Village_Tracking.xlsx")) #Old method

village_details <- read_sheet("https://docs.google.com/spreadsheets/d/1iWDd8k6L5Ny6KklxEnwvGZDkrAHBd0t67d-29BfbMGo/edit?pli=1#gid=1710429467")


#endline census
#el <- read_stata(paste0(user_path(),"3_final/1_8_Endline_Census_cleaned.dta" ))
el <- read_stata(paste0(user_path(),"/3_final/1_10_Endline_Census_HH_clean_consented.dta"))


#map data - shapefile
shp_file_0 <- st_read(paste0(user_path(), "7_map/shapefiles/gadm41_IND_0.shp"), quiet = TRUE)
shp_file_1 <- st_read(paste0(user_path(), "7_map/shapefiles/gadm41_IND_1.shp"), quiet = TRUE)
shp_file_2 <- st_read(paste0(user_path(), "7_map/shapefiles/gadm41_IND_2.shp"), quiet = TRUE)
shp_file_3 <- st_read(paste0(user_path(), "7_map/shapefiles/gadm41_IND_3.shp"), quiet = TRUE)




```

# Defining Functions

```{r defining misc functions}

source(paste0(github_path(),"/3_manuscript/1-functions.R"))

```

# Data Cleaning

```{r Data cleaning R code}

#Calling script to clean loaded data
source(paste0(github_path(),"/3_manuscript/India ILC Pilot - Manuscript Data Cleaning 2024.R"))


```


```{r saving datasets}


#Baseline Census

#Selecting key variables for analysis only
cen <- cen%>%
  dplyr::select(unique_id, village, village_ID, block, BlockCode, panchayat_village, assignment,
         hhhead_gender_binary, hhmember_count, read_write_binary, prim_source,
         prim_source_jjm, prim_source_ctap,
         prim_source_surface, prim_source_well, prim_source_borehole, prim_source_other, 
         sec_source, jjm_drinking, 
         water_treat_binary, electricity_binary, tv_binary, mobile_binary, 
         fridge_binary, motorcycle_binary)


#Baseline Survey

bl <- bl%>%
  dplyr::select(unique_id, village, village_ID, block, `Block code`, panchayat_village, assignment,
                water_source_prim, water_sec_yn, treat_water_before, treat_time_category,
                treat_time_5min, sample_ID_tap, sample_ID_stored,
                fc_stored, fc_stored_binary, fc_tap, fc_tap_binary, tc_stored,
                tc_stored_binary,tc_tap, tc_tap_binary)


#Endline census
el <- el%>%
  dplyr::select(unique_id, village, village_ID, block, BlockCode, panchayat_village, assignment,
                prim_source, time_spent_treat_5,
                prim_source_jjm, sec_source, jjm_drinking, water_treat_binary,
                time_spent_treat_5, tap_issues_taste
                )


#IDEXX
#idexx_tab no changes needed

#Weekly Monitoring
#mon_summary no changes needed
#mon_summary_weekly no changes needed


  write_csv(cen,paste0(user_path(), "3_final/manuscript_datasets/", "1_1_baseline_census.csv"))
  write_csv(bl,paste0(user_path(), "3_final/manuscript_datasets/", "1_1_baseline_survey.csv"))
  write_csv(el,paste0(user_path(), "3_final/manuscript_datasets/", "1_8_endline_census.csv"))
  write_csv(idexx_tab, paste0(user_path(), "3_final/manuscript_datasets/", "1_10_idexx_all_rounds.csv"))
  write_csv(mon_summary,
            paste0(user_path(), "3_final/manuscript_datasets/", "1_11_weekly_monitoring.csv"))


```




# Baseline Desc Stats

```{r Baseline Desc Stats Code}

  

# Define function to calculate standard error for proportions
calculate_se <- function(p, n) {
  sqrt((p * (1 - p)) / n)
}

# Identify variable types
binary_categorical_vars <- c("hhhead_gender_binary", "read_write_binary", 
                             "sec_source", "jjm_drinking", "water_treat_binary", 
                             "electricity_binary", "tv_binary", "mobile_binary", 
                             "fridge_binary", "motorcycle_binary")

multi_level_categorical_vars <- c("prim_source")  # Multi-category variable
continuous_vars <- c("hhmember_count")

# Convert binary categorical variables (character) to numeric (1 = "yes", 0 = "no")
cen <- cen %>%
  mutate(across(all_of(binary_categorical_vars), 
                ~ case_when(. %in% c("yes", "Yes", "1") ~ 1,
                            . %in% c("no", "No", "0") ~ 0,
                            TRUE ~ NA_real_)))  # Ensures missing values remain as NA

# Compute stats for binary categorical variables (Proportion + SE)
binary_categorical_summary_cen <- cen %>%
  select(all_of(binary_categorical_vars), assignment) %>%
  pivot_longer(cols = all_of(binary_categorical_vars), names_to = "variable", values_to = "value") %>%
  group_by(variable, assignment) %>%
  summarise(
    n = sum(!is.na(value)),  # Count non-missing values
    p = mean(value, na.rm = TRUE),  # Proportion
    se = calculate_se(p, n),  # Standard error
    formatted_stat = sprintf("%.1f%% (%.1f)", p * 100, se * 100),
    .groups = "drop"
  ) %>%
  select(variable, assignment, formatted_stat)

# Identify variable types
#Baseline followup survey desc stats
binary_categorical_vars <- c("fc_tap_binary", "fc_stored_binary",
                  #"cf_pa_binary1","cf_pa_binary2","ec_pa_binary1","ec_pa_binary2",#"water_treat_binary",
                  "tap_taste_binary", "treat_time_5min")


# Compute stats for binary categorical variables (Proportion + SE)
binary_categorical_summary_bl <- bl%>%
  select(all_of(binary_categorical_vars), assignment) %>%
  pivot_longer(cols = all_of(binary_categorical_vars), names_to = "variable", values_to = "value") %>%
  group_by(variable, assignment) %>%
  summarise(
    n = sum(!is.na(value)),  # Count non-missing values
    p = mean(value, na.rm = TRUE),  # Proportion
    se = calculate_se(p, n),  # Standard error
    formatted_stat = sprintf("%.1f%% (%.1f)", p * 100, se * 100),
    .groups = "drop"
  ) %>%
  select(variable, assignment, formatted_stat)



# Compute stats for multi-category variables (Each level as a proportion)
multi_categorical_summary <- cen %>%
  select(all_of(multi_level_categorical_vars), assignment) %>%
  pivot_longer(cols = all_of(multi_level_categorical_vars), names_to = "variable", values_to = "value") %>%
  group_by(variable, assignment) %>% 
  mutate(total = n()) %>%  # Calculate total responses per treatment group
  group_by(variable, value, assignment) %>%  # Now group by category level
  summarise(
    n = n(),  # Count per category level
    total = unique(total),  # Correctly get the total responses for that treatment group
    p = n / total,  # Proportion of each level within treatment
    se = calculate_se(p, total),  # Standard error
    formatted_stat = sprintf("%.1f%% (%.1f)", p * 100, se * 100),
    .groups = "drop"
  ) %>%
  rename(category = value) %>%
  mutate(variable = paste0(variable, " - ", category)) %>%  # Append category name
  select(variable, assignment, formatted_stat)

# Compute stats for continuous variables (Mean + SD)
continuous_summary <- cen %>%
  select(all_of(continuous_vars), assignment) %>%
  pivot_longer(cols = all_of(continuous_vars), names_to = "variable", values_to = "value") %>%
  group_by(variable, assignment) %>%
  summarise(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    formatted_stat = sprintf("%.1f (%.1f)", mean, sd),
    .groups = "drop"
  ) %>%
  select(variable, assignment, formatted_stat)




#Separating stored vs tap water tests ------

idexx_bl_tap <- idexx%>%
  filter(sample_type == "Tap")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_tap = "cf_pa_binary")%>%
  rename(ec_pa_tap = "ec_pa_binary")%>%
  rename(cf_log_tap = "cf_log")%>%
  rename(ec_log_tap = "ec_log")

idexx_bl_stored <- idexx%>%
  filter(sample_type == "Stored")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_stored = "cf_pa_binary")%>%
  rename(ec_pa_stored = "ec_pa_binary")%>%
  rename(cf_log_stored = "cf_log")%>%
  rename(ec_log_stored = "ec_log")


#Baseline followup survey desc stats
binary_categorical_vars <- c("ec_pa_tap", "cf_pa_tap"
                  )


# Compute stats for binary categorical variables (Proportion + SE)
binary_categorical_summary_tap <- idexx_bl_tap%>%
  select(all_of(binary_categorical_vars), assignment) %>%
  pivot_longer(cols = all_of(binary_categorical_vars), names_to = "variable", values_to = "value") %>%
  group_by(variable, assignment) %>%
  summarise(
    n = sum(!is.na(value)),  # Count non-missing values
    p = mean(value, na.rm = TRUE),  # Proportion
    se = calculate_se(p, n),  # Standard error
    formatted_stat = sprintf("%.1f%% (%.1f)", p * 100, se * 100),
    .groups = "drop"
  ) %>%
  select(variable, assignment, formatted_stat)


#Baseline followup survey desc stats
binary_categorical_vars <- c("ec_pa_stored", "cf_pa_stored"
                  #"cf_pa_binary1","cf_pa_binary2","ec_pa_binary1","ec_pa_binary2",#"water_treat_binary
                  )


# Compute stats for binary categorical variables (Proportion + SE)
binary_categorical_summary_stored <- idexx_bl_stored%>%
  select(all_of(binary_categorical_vars), assignment) %>%
  pivot_longer(cols = all_of(binary_categorical_vars), names_to = "variable", values_to = "value") %>%
  group_by(variable, assignment) %>%
  summarise(
    n = sum(!is.na(value)),  # Count non-missing values
    p = mean(value, na.rm = TRUE),  # Proportion
    se = calculate_se(p, n),  # Standard error
    formatted_stat = sprintf("%.1f%% (%.1f)", p * 100, se * 100),
    .groups = "drop"
  ) %>%
  select(variable, assignment, formatted_stat)



#Continuous variables microbial contamination results
continuous_vars <- c("ec_log_tap", "cf_log_tap")


# Compute stats for continuous variables (Mean + SD)
continuous_summary_tap <- idexx_bl_tap %>%
  select(all_of(continuous_vars), assignment) %>%
  pivot_longer(cols = all_of(continuous_vars), names_to = "variable", values_to = "value") %>%
  group_by(variable, assignment) %>%
  summarise(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    formatted_stat = sprintf("%.1f (%.2f)", mean, sd),
    .groups = "drop"
  ) %>%
  select(variable, assignment, formatted_stat)

#Continuous variables microbial contamination results
continuous_vars <- c("ec_log_stored", "cf_log_stored")


# Compute stats for continuous variables (Mean + SD)
continuous_summary_stored <- idexx_bl_stored%>%
  select(all_of(continuous_vars), assignment) %>%
  pivot_longer(cols = all_of(continuous_vars), names_to = "variable", values_to = "value") %>%
  group_by(variable, assignment) %>%
  summarise(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    formatted_stat = sprintf("%.1f (%.2f)", mean, sd),
    .groups = "drop"
  ) %>%
  select(variable, assignment, formatted_stat)







# Combine all summaries
desc_stats_cen <- bind_rows(binary_categorical_summary_cen, multi_categorical_summary, continuous_summary, binary_categorical_summary_bl, binary_categorical_summary_tap, binary_categorical_summary_stored, continuous_summary_tap,continuous_summary_stored) %>%
  pivot_wider(names_from = assignment, values_from = formatted_stat)

# Convert to gt table
desc_stats_cen %>%
  gt() %>%
  tab_header(title = "Descriptive Statistics with Standard Errors")



```




\newpage
# Baseline Household Characteristics

```{r Baseline household characteristics}


#Baseline Census Desc Stats
outcome_vars <- c("assignment","hhmember_count", "hhhead_gender",
                  "read_write_1", "prim_source", "sec_source","jjm_drinking", "water_treat_binary",
                  "electricity_binary", "tv_binary","mobile_binary", "fridge_binary",
                  "motorcycle_binary")

#GT method
#Summarizing desc stats for each variable
#reset_gtsummary_theme()
desc_stats_cen <- cen%>%
  dplyr::select(all_of(outcome_vars))%>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    # type = list(c("hhmember_count","sec_source"
                    #          "water_treat_binary") ~ "continuous",
                    #         c("hhhead_gender", "read_write_1",
                    #          "mobile","electricity", "prim_source") ~ "categorical"
                    #         ),
                    
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 1, 
                                  all_categorical() ~ 1),
                    label = list(hhmember_count ~ "Average household size",
                                 hhhead_gender ~ "Household head gender",
                                 read_write_1 ~ "Respondent can read and write",
                                 prim_source ~ "Primary drinking water source",
                                 sec_source ~ "Uses a secondary drinking water source",
                                 jjm_drinking ~ "Drink water from their tap connection",
                                 water_treat_binary ~ "Treats drinking water",
                                 electricity_binary ~ "Has electricity",
                                 tv_binary ~ "Owns a TV",
                                 mobile_binary ~ "Owns a cell phone",
                                 fridge_binary ~ "Owns a refrigerator",
                                 motorcycle_binary ~ "Owns a motorbike or scooter"
                                 )
                    )%>%
  add_n()

desc_stats_cen_gt <- as_tibble(desc_stats_cen)%>%
  gt::gt()

# desc_stats_cen_gt%>%
#   gtsave(path = (paste0(github_path(), "/3_manuscript/figures")), filename = "desc_stats_cen.pdf")

desc_stats_cen_df <- desc_stats_cen%>%
  as.data.frame()%>%
  rename("Treatment" = `**Treatment**  \nN = 423`)%>%
  rename("Control" = `**Control**  \nN = 491`)




#Baseline followup survey desc stats
outcome_vars <- c("assignment", "fc_tap_binary", "fc_stored_binary",
                  #"cf_pa_binary1","cf_pa_binary2","ec_pa_binary1","ec_pa_binary2",
                  "water_treat_binary",
                  "treat_time_category", "tap_taste_binary", "treat_time_5min")

desc_stats_bl <- bl%>%
  dplyr::select(all_of(outcome_vars))%>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    # type = list(c("hhmember_count","sec_source"
                    #          "water_treat_binary") ~ "continuous",
                    #         c("hhhead_gender", "read_write_1",
                    #          "mobile","electricity", "prim_source") ~ "categorical"
                    #         ),
                    
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 1, 
                                  all_categorical() ~ 1),
                    label = list(
                                 fc_tap_binary ~ "Presence of free chlorine at tap connection",
                                 fc_stored_binary ~ "Presence of free chlorine in stored water",
                                 # cf_pa_binary1 ~ "Presence of total coliform in tap water",
                                 # cf_pa_binary2 ~ "Presence of total coliform in stored water",
                                 # ec_pa_binary1 ~ "Presence of E. coli in tap water",
                                 # ec_pa_binary2 ~ "Presence of E. coli in stored water",
                                 #water_treat_binary ~ "Treats drinking water",
                                 treat_time_category ~ "Time spent treating water",
                                 treat_time_5min ~ "Time spent treating water > 5 min",
                                 tap_taste_binary ~ "Satisfied with taste of tap water"
                                 )
                    )%>%
  add_n()

desc_stats_bl_gt <- as_tibble(desc_stats_bl)%>%
  gt::gt()

# desc_stats_bl_gt%>%
#   gtsave(path = (paste0(github_path(), "/3_manuscript/figures")), filename = "desc_stats_bl.pdf")

desc_stats_bl_df <- desc_stats_bl%>%
  as.data.frame()%>%
  rename("Treatment" = `**Treatment**  \nN = 100`)%>%
  rename("Control" = `**Control**  \nN = 100`)


#Separating stored vs tap water tests ------

idexx_bl_tap <- idexx%>%
  filter(sample_type == "Tap")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_tap = "cf_pa_binary")%>%
  rename(ec_pa_tap = "ec_pa_binary")%>%
  rename(cf_log_tap = "cf_log")%>%
  rename(ec_log_tap = "ec_log")

idexx_bl_stored <- idexx%>%
  filter(sample_type == "Stored")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_stored = "cf_pa_binary")%>%
  rename(ec_pa_stored = "ec_pa_binary")%>%
  rename(cf_log_stored = "cf_log")%>%
  rename(ec_log_stored = "ec_log")



#Summarizing desc stats --------------------------------------

#Tap water
desc_stats_bl_tap <- idexx_bl_tap%>%
  dplyr::select(assignment, cf_pa_tap, ec_pa_tap, 
                cf_log_tap, ec_log_tap
                )%>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("cf_pa_tap", "ec_pa_tap",
                             "cf_log_tap","ec_log_tap"
                             ) ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 1, 
                                  all_categorical() ~ 1),
                    label = list(cf_pa_tap ~ "Tap - Presence/Absence of Total Coliform",
                                 ec_pa_tap ~ "Tap - Presence/Absence of E. coli",
                                 cf_log_tap ~ "Tap - Mean Log10 of Total Coliform",
                                 ec_log_tap ~ "Tap - Mean Log10 of E. coli"
                                )
                    )%>%
  add_n()%>%
  as.data.frame()%>%
  rename("Treatment" = `**Treatment**  \nN = 40`)%>%
  rename("Control" = `**Control**  \nN = 40`)


#Stored water
desc_stats_bl_stored <- idexx_bl_stored%>%
  dplyr::select(assignment, cf_pa_stored, ec_pa_stored, cf_log_stored, ec_log_stored
                )%>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("cf_pa_stored", "ec_pa_stored",
                             "cf_log_stored", "ec_log_stored"
                             ) ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 1, 
                                  all_categorical() ~ 1),
                    label = list(cf_pa_stored ~ "Stored - Presence/Absence of Total Coliform",
                                 ec_pa_stored ~ "Stored - Presence/Absence of E. coli",
                                 cf_log_stored ~ "Stored - Mean Log10 of Total Coliform",
                                 ec_log_stored ~ "Stored - Mean Log10 of E. coli"
                                )
                    )%>%
  add_n()%>%
  as.data.frame()%>%
  rename("Treatment" = `**Treatment**  \nN = 40`)%>%
  rename("Control" = `**Control**  \nN = 40`)


#Recombining tables
desc_stats_bl <- bind_rows(desc_stats_cen_df, desc_stats_bl_df)%>% 
  bind_rows(desc_stats_bl_tap)%>%
  bind_rows(desc_stats_bl_stored)%>%
  as_tibble()%>%
  gt::gt()

desc_stats_bl%>%
  gtsave(path = (paste0(github_path(), "/3_manuscript/figures")), filename = "desc_stats_bl.pdf")




#Manual Desc Stat Method
#
# outcome_vars <- c("hhmember_count", "hhhead_gender",
#                   "read_write_1", "prim_source", "sec_source", "water_treat_binary")
# 
# desc_stats <- compute_desc_stats(data = cen, vars = outcome_vars,
#                                  treatment_col = "assignment")
# 
# 
# kable <- present_desc_stats_kable(desc_stats, treatment_col = "assignment")
# 
# 
# ft <- present_desc_stats_flextable(desc_stats, treatment_col = "assignment")
# 









```
\newpage
# Baseline Balance

```{r Baseline Balance}



#Baseline Balance -----

#Baseline Census
# outcome_vars <- c("hhmember_count",
#                   "hhhead_gender",
#                   "read_write_1",
#                   "prim_source",
#                   "sec_source",
#                   "water_treat_binary")

outcome_vars <- c("hhmember_count","read_write_1", "prim_source", "sec_source",
                  "jjm_drinking", "water_treat_binary",
                  "electricity_binary", "tv_binary","mobile_binary", "fridge_binary",
                  "motorcycle_binary")

cen_model <- factormaker(cen, outcome_vars)

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = cen_model, var)
                 }
                  )
# #linear regression
# all_models <- lapply(outcome_vars, 
#                      function(var){ #This functions "subsets" the ilc_glm function
#                        ilc_lm(data = el_tab, var)
#                      }
#                        )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
ilc_model_table(all_models)



#Baseline followup survey ----
outcome_vars <- c("fc_tap_binary", "fc_stored_binary",
                  #"cf_pa_binary1","cf_pa_binary2","ec_pa_binary1","ec_pa_binary2",
                  "treat_time_category", "tap_taste_binary")


bl_model <- factormaker(bl, outcome_vars)


#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = bl_model, var)
                 }
                  )


#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
ilc_model_table(all_models)




# Microbial Contamination - Baseline Balance -------------------------------------------------

#Separating by tap and stored water
idexx_bl_tap <- idexx%>%
  filter(sample_type == "Tap")

idexx_bl_stored <- idexx%>%
  filter(sample_type == "Stored")
  

#Running Poisson Regression on Tap Samples ----


outcome_vars <- c("cf_pa_binary","ec_pa_binary") #Selecting outcome variables

idexx_model <- factormaker(idexx_bl_tap, outcome_vars) #Converting to numeric type

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_tap <- ilc_model_table_only(all_models)
idexx_poisson_tap <- idexx_poisson_tap%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_tap", "ec_tap"))%>%
  mutate(sample_type = "Tap")


#Running Poisson Regression on Stored Samples ----

outcome_vars <- c("cf_pa_binary","ec_pa_binary") #Selecting outcome variables

idexx_model <- factormaker(idexx_bl_stored, outcome_vars) #Converting to numeric type

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_stored <- ilc_model_table_only(all_models)
idexx_poisson_stored <- idexx_poisson_stored%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_stored", "ec_stored"))%>%
  mutate(sample_type = "Stored")


idexx_poisson_bl <- rbind(idexx_poisson_tap, idexx_poisson_stored)




#Running Linear Regression on Tap Samples ----


outcome_vars <- c("cf_log","ec_log") #Selecting outcome variables

idexx_model <- idexx_bl_tap


#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_lm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_lm_tap <- ilc_model_lm_table_only(all_models)
idexx_lm_tap <- idexx_lm_tap%>%
  mutate(sample_type = "Tap")


#Running Poisson Regression on Stored Samples ----

outcome_vars <- c("cf_log","ec_log") #Selecting outcome variables

idexx_model <- idexx_bl_stored

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_lm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_lm_stored <- ilc_model_lm_table_only(all_models)
idexx_lm_stored <- idexx_lm_stored%>%
  mutate(sample_type = "Stored")


idexx_lm_bl <- rbind(idexx_lm_tap, idexx_lm_stored)

idexx_lm_bl










#Checking unadjusted balance on E. coli measurements in tap samples
outcome_vars <- c("ec_pa_binary") #Selecting outcome variables

idexx_model <- factormaker(idexx_bl_tap, outcome_vars) #Converting to numeric type

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm_unadj(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_tap <- ilc_model_table_only(all_models)
idexx_poisson_tap <- idexx_poisson_tap%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_tap", "ec_tap"))%>%
  mutate(sample_type = "Tap")





```


\newpage
# Weekly Chlorine Monitoring

```{r Weekly Chlorine Monitoring}


#Summary of monitoring data across all villages
  
cl_p1 <- ggplot(data = mon_summary_weekly) + 
    geom_errorbar(aes(x = test_week, ymin = lower_ci, ymax = upper_ci),
                  width = 2) + #Does not include robust standard errors for village clustering
    geom_point(aes(x = test_week, y = avg_concentration))+
    geom_line(aes(x = test_week, y = avg_concentration))+
    geom_hline(yintercept=0.20, linetype="dashed", color = "red")+
    geom_hline(yintercept=0.60, linetype="dashed", color = "red")+
    scale_y_continuous(
                     limits = c(0, 2.0),
                     expand = c(0,0))+
  scale_x_date(
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
    labs(x = "Date", 
       y = "Free Chlorine Concentration (mg/L)",
       color = "Sample Type",
       title = (paste0("Chlorine Monitoring - February-October 2024")),
       caption = "Concentrations were averaged on a weekly-basis across the 10 treatment villages.")+
    theme_bw() + 
    theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))
  
  
cl_p1


#Summary of proportion of positive samples across all villages over time
  
cl_p2 <- ggplot(data = mon_summary_weekly) + 
    #geom_errorbar(aes(x = test_week, ymin = lower_ci_pa, ymax = upper_ci_pa),
     #             width = 2) + #Does not include robust standard errors for village clustering
    geom_col(aes(x = test_week, y = cl_presence))+
  geom_text(aes(x = ymd("2024-06-02"), y = 7, label = "NA"),
            position = position_dodge(width = 0.7), size = 3)+
  geom_text(aes(x = ymd("2024-06-30"), y = 7, label = "NA"),
            position = position_dodge(width = 0.7), size = 3)+
    scale_y_continuous(
                     limits = c(0, 100.0),
                     expand = c(0,0))+
  scale_x_date(
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
    labs(x = "Date", 
       y = "Proportion of Samples Positive for Free Chlorine (> 0.1 mg/L)",
       title = (paste0("Chlorine Monitoring - February-October 2024")),
       caption = "Concentrations were averaged across 2 taps in each village on a weekly-basis across the 10 treatment villages.")+
    theme_bw() + 
    theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))
  
  
cl_p2




#Calculating # of no dosing events

mon_no_dosing <- mon%>%
  filter(chlorine_concentration < 0.10)%>%
  filter(chlorine_test == "Nearest Tap" | chlorine_test == "Farthest Tap")

mon_no_dosing <- mon_no_dosing%>%
  group_by(test_date, village_name)%>%
  summarise(no_dosing_events = n())
  




```
\newpage
# Longitudinal Chlorine Monitoring

```{r Longitudinal Chlorine Monitoring}


# p_mon_long <- ggplot(data = mon_long) +
#   geom_point(aes(x = time, y = tw_fc, color = factor(location))) +
#   geom_line(aes(x = time, y = tw_fc, color = factor(location), group = location)) +
#   facet_wrap(~ village_code, scales = "free_x") +
#   geom_hline(yintercept = 0.20, linetype = "dashed", color = "red") +
#   geom_hline(yintercept = 0.60, linetype = "dashed", color = "red") +
#   labs(
#     title = "Longitudinal Chlorine Monitoring Over Water Supply Time",
#     x = "Time of Sample Collection",
#     y = "Free Chlorine Concentration (mg/L)",
#     color = "Sampling Location"
#   ) +
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1),
#     legend.position = "bottom",
#     strip.text = element_text(size = 12)
#   ) +
#   scale_y_continuous(
#     limits = c(0, 1),
#     breaks = seq(from = 0.0, to = 1.0, by = 0.2)
#   ) 
# 
# 
# p_mon_long


```


\newpage
# Follow-up Surveys WASH Variables

```{r Follow up surveys WASH variables}

#Removing baseline round data
fu_rounds <- all_rounds%>%
  filter(data_round != "BL")



#WASH Variables ---- 
#Summarizing data and running regression models ----

#Selecting outcome variables
outcome_vars <- c("prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary",
                 "tap_trust_binary", "tap_taste_binary", "tap_future_binary",
                 "fc_tap_binary", "fc_stored_binary")



#GT method
#Summarizing desc stats for each variable
#reset_gtsummary_theme()

# desc_stats <- fu_rounds%>%
#   dplyr::select("assignment","data_round","prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary","tap_trust_binary", "tap_taste_binary", "tap_future_binary","fc_tap_binary", "fc_stored_binary")%>%
#   tbl_strata(
#     strata = data_round,
#     .tbl_fun =
#       ~ .x %>%
#         tbl_summary(by = assignment, 
#                     missing = "no",
#                     type = c("prim_source_jjm", "sec_source", "jjm_drinking",
#                              "water_treat_binary", "tap_trust_binary", "tap_taste_binary",
#                              "tap_future_binary","fc_tap_binary",
#                              "fc_stored_binary") ~ "continuous",
#                     statistic = list(
#                       all_continuous() ~ "{mean} ({sd})",
#                       all_categorical() ~ "{p}%"),
#                     digits = list(all_continuous() ~ 2, 
#                                   all_categorical() ~ 0),
#                     label = list(prim_source_jjm ~ "Government-provided tap as primary source",
#                                  sec_source ~ "Use of a secondary source",
#                                  jjm_drinking ~ "Use of government-provided taps for drinking",
#                                  water_treat_binary ~ "Water treatment used",
#                                  tap_trust_binary ~ "Trust in safety of taps",
#                                  tap_taste_binary ~ "Satisfaction with taste from taps",
#                                  tap_future_binary ~ "Likelihood of using taps in future",
#                                  fc_tap_binary ~ "Presence of free chlorine in taps (>0.1 mg/L)",
#                                  fc_stored_binary ~ "Presence of free chlorine in stored water (>0.1 mg/L)"
#                                  )
#                     )%>%
#      modify_footnote(all_stat_cols() ~ "Mean (SD)"),
#     .header = "**{strata}**"
#   )%>%
#   modify_footnote(update =  ~ "Mean (SD); BL - Oct 2023, R1 - February 2024, R2 - March 2024, R3 - April 2024")

# desc_stats <- as_gt(desc_stats)%>%
#   tab_options(table.font.size = 11)


# Poisson Regression - Treatment Effect -------------------------------------------------



outcome_vars <- c("prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary",
                 "tap_trust_binary", "tap_taste_binary", "tap_future_binary",
                 "fc_tap_binary", "fc_stored_binary")

fu_model <- factormaker(fu_rounds, outcome_vars)

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = fu_model, var)
                 }
                  )
# #linear regression
# all_models <- lapply(outcome_vars, 
#                      function(var){ #This functions "subsets" the ilc_glm function
#                        ilc_lm(data = el_tab, var)
#                      }
#                        )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
ilc_model_table(all_models)





```




\newpage
# Follow-up Surveys Chlorine and Microbiological Contamination

```{r Followup Surveys - Chlorine and Microbiological Contamination}


# Microbiological contamination ------------------------------------------------

#Separating out follow-up rounds
idexx_fu <- idexx_tab%>%
  filter(data_round != "BL")

#Separating stored vs tap water tests ------
idexx_ids <- idexx_tab%>%
  dplyr::select(assignment, village, block, panchayat_village, data_round, sample_ID, bag_ID_tap, bag_ID_stored)

idexx_tab_tap <- idexx_tab%>%
  filter(sample_type == "Tap")%>%
  #filter(pooled_round == "FU")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, data_round, pooled_round, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_tap = "cf_pa_binary")%>%
  rename(ec_pa_tap = "ec_pa_binary")%>%
  rename(cf_log_tap = "cf_log")%>%
  rename(ec_log_tap = "ec_log")

idexx_tab_stored <- idexx_tab%>%
  filter(sample_type == "Stored")%>%
  #filter(pooled_round == "FU")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, data_round, pooled_round, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_stored = "cf_pa_binary")%>%
  rename(ec_pa_stored = "ec_pa_binary")%>%
  rename(cf_log_stored = "cf_log")%>%
  rename(ec_log_stored = "ec_log")



#Summarizing desc stats --------------------------------------

#Tap water

desc_stats <- idexx_tab_tap%>%
  dplyr::select(assignment, data_round, cf_pa_tap, ec_pa_tap, cf_log_tap, ec_log_tap
                )%>%
  tbl_strata(
    strata = data_round,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("cf_pa_tap", "ec_pa_tap", "cf_log_tap",
                             "ec_log_tap") ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(cf_pa_tap ~ "Tap - Presence/Absence of Total Coliform",
                                 ec_pa_tap ~ "Tap - Presence/Absence of E. coli",
                                 cf_log_tap ~ "Tap - Mean Log10 of Total Coliform",
                                 ec_log_tap ~ "Tap - Mean Log10 of E. coli"
                                )
                    )%>%
     modify_footnote(all_stat_cols() ~ "Mean (SD)"),
    .header = "**{strata}**"
  )%>%
  modify_footnote(update =  ~ "Mean (SD); BL - Baseline, FU - Followup")

# desc_stats_tap <- as_gt(desc_stats)%>%
#   tab_options(table.font.size = 11)

#desc_stats_tap



#Stored water
desc_stats <- idexx_tab_stored%>%
  dplyr::select(assignment, data_round, cf_pa_stored, ec_pa_stored, cf_log_stored, ec_log_stored
                )%>%
  tbl_strata(
    strata = data_round,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("cf_pa_stored", "ec_pa_stored", "cf_log_stored",
                             "ec_log_stored") ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(cf_pa_stored ~ "Stored - Presence/Absence of Total Coliform",
                                 ec_pa_stored ~ "Stored - Presence/Absence of E. coli",
                                 cf_log_stored ~ "Stored - Mean Log10 of Total Coliform",
                                 ec_log_stored ~ "Stored - Mean Log10 of E. coli"
                                )
                    )%>%
     modify_footnote(all_stat_cols() ~ "Mean (SD)"),
    .header = "**{strata}**"
  )%>%
  modify_footnote(update =  ~ "Mean (SD); BL - Baseline, FU - Followup")

#desc_stats_stored <- as_gt(desc_stats)%>%
  #tab_options(table.font.size = 11)

#desc_stats_stored


#Creating desc stat figures ------------------------------------------------


#Calculating key desc stats -- pooled rounds and baseline
tc_stats_pooled <- pooled_stats(idexx_fu)

tc_stats_bl <- pooled_stats(idexx)

tc_stats_round <- round_stats(idexx_tab)

all_stats_bl <- all_stats(idexx)

#Calculating desc stats by village
# tc_stats_village <- idexx_tab%>%
#   group_by(village)%>%
#   summarise("Number of Samples" = n(),
#       "% Positive for Total Coliform" = round((sum(cf_pa == "Presence") / n()) * 100, 1),
#       "% Positive for E. coli" = round((sum(ec_pa == "Presence") / n()) * 100, 1),
#       "SD E. coli" = sd(ec_pa_binary)
#       )
#   
# mean(tc_stats_village$`% Positive for E. coli`)


#Creating figure of baseline IDEXX results

#Plotting treatment/control stats on a bar plot
p_ec_bl <- ggplot(data = tc_stats_bl) + 
  geom_point(aes(x = sample_type, y = `% Positive for E. coli`, color = assignment), 
           position = position_dodge(width = 0.35), size = 3) +
   geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     color = assignment), position = position_dodge(width = 0.35),
                 width = .2) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       color = "Assignment",
       title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 160)")),
  caption = "Stored and tap water samples were collected during the baseline survey round in October 2023."
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_classic() + 
  theme(axis.text.x = element_text(vjust=1))

p_ec_bl

#ggsave(filename = "manuscript_ecoli_baseline_results.jpeg", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 4, height = 2, units = "in", scale = 2.6)



p_cf_bl <- ggplot(data = tc_stats_bl) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "",
       caption = ""
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

#Patchwork package addition
p_bl <- 
  p_cf_bl + p_ec_bl +
  plot_annotation(
  title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 160)")),
  caption = "Stored and tap water samples were collected during the baseline survey round in October 2023."
)

p_bl





#Creating figure of pooled IDEXX results

#Plotting treatment/control stats on a bar plot
p_ec_pooled <- ggplot(data = tc_stats_pooled) + 
  geom_point(aes(x = sample_type, y = `% Positive for E. coli`, color = assignment), 
           position = position_dodge(width = 0.35), size = 3) +
   geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     color = assignment), position = position_dodge(width = 0.35),
                 width = .2) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       color = "Assignment",
       title = expression(paste("Presence of ", italic("E. coli"), " in Household Drinking Water (N = 961)")),
  caption = "Stored and tap water samples were pooled across 6 household surveys rounds across 20 villages in February, March, April, August, September, and October 2024."
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_classic() + 
  theme(axis.text.x = element_text(vjust=1))

p_cf_pooled <- ggplot(data = tc_stats_pooled) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "",
       caption = ""
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(vjust=1, hjust=1))

#Patchwork package addition
p_pooled <- 
  p_cf_pooled + p_ec_pooled +
  plot_annotation(
  title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 961)")),
  caption = "Stored and tap water samples were pooled across 6 household surveys rounds across 20 villages in February, March, April, August, September, and October 2024."
)

p_pooled

#ggsave(filename = "manuscript_ecoli_pooled_results.jpeg", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 4, height = 2, units = "in", scale = 2.6)





#Combining baseline results and pooled results into one figure
p_ec <- p_ec_bl + p_ec_pooled
p_ec

ggsave(filename = "manuscript_ecoli_results.pdf", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 3.5, height = 1.5, units = "in", scale = 2)








#Creating figure of IDEXX results stratified by round

#Tap samples -----------------------------------------------
#Plotting treatment/control stats on a bar plot
p_ec_by_round <- tc_stats_round%>%
  #filter(sample_type == "Tap")%>%
  ggplot() + 
  geom_col(aes(x = data_round_month, y = `% Positive for E. coli`, fill = assignment), position = "dodge") +
  geom_errorbar(aes(x = data_round_month, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                    fill = assignment), position = position_dodge(width = 27),
                width = 10) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  scale_x_date(
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
  labs(x = "Date", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  facet_wrap(~ sample_type)+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_by_round <- tc_stats_round%>%
  #filter(sample_type == "Tap")%>%
  ggplot() + 
  geom_col(aes(x = data_round_month, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = data_round_month, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 27),
                 width = 10) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
    scale_x_date(
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
  labs(x = "Date", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "",
       caption = ""
       )+
  facet_wrap(~ sample_type)+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

#Patchwork package addition
p_by_round <- 
  p_cf_by_round + p_ec_by_round +
  plot_annotation(
  title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 960)")),
  caption = "Stored and tap water samples were pooled across 5 monthly household surveys rounds across 20 villages in February, March, and April, July, and August 2024."
)

p_by_round


#Creating box plot of log MPN counts across rounds
# 
# #Plotting treatment/control stats on a bar plot
# p_ec_by_round <- ggplot(data = idexx_tab) + 
#   geom_boxplot(aes(x = sample_type, y = ec_log, fill = assignment)) +
#   scale_y_continuous(
#                      limits = c(-0.5, 4),
#                      expand = c(0,0))+
#   labs(x = "Sample Type", 
#        y = expression(paste("Log10 MPN ",italic("E. coli"), " per 100 mL")),
#        fill = "Assignment",
#        title = "",
#        caption = ""
#        #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
#        )+
#   facet_wrap(~ data_round)+
#   theme_bw() + 
#   theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))
# 
# p_cf_by_round <- ggplot(data = idexx_tab) + 
#   geom_boxplot(aes(x = sample_type, y = cf_log, fill = assignment), position = "dodge") +
#   #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
#   scale_y_continuous(
#                      limits = c(-0.5, 4),
#                      expand = c(0,0))+
#   labs(x = "Sample Type", 
#        y = expression(paste("Log10 MPN Total Coliform per 100 mL")),
#        fill = "Assignment",
#        title = "",
#        caption = ""
#        )+
#   facet_wrap(~ data_round)+
#   theme_bw() + 
#   theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))
# 
# #Patchwork package addition
# p_by_round <- 
#   p_cf_by_round + p_ec_by_round +
#   plot_annotation(
#   title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 960)")),
#   caption = "Stored and tap water samples were pooled across 5 monthly household surveys rounds across 20 villages in February, March, and April, July, and August 2024."
# )
# 
# p_by_round


#Creating plot of pooled results from the monsoon rounds
tc_stats_monsoon <- tc_stats_round%>%
  filter(data_round == "R4" | data_round == "R5" | data_round == "R6")

#Plotting treatment/control stats on a bar plot
p_ec_monsoon <- ggplot(data = tc_stats_monsoon) + 
  geom_col(aes(x = sample_type, y = `% Positive for E. coli`, fill = assignment), position = "dodge") +
  geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                    fill = assignment), position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  facet_wrap(~ data_round)+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_monsoon <- ggplot(data = tc_stats_monsoon) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "",
       caption = ""
       )+
  facet_wrap(~ data_round)+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

#Patchwork package addition
p_monsoon <- 
  p_cf_monsoon + p_ec_monsoon +
  plot_annotation(
  title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 320)")),
  caption = "Stored and tap water samples were pooled across 6 monthly household surveys rounds across 20 villages in February, March, and April, July, and August 2024."
)

p_monsoon



#Presenting WHO risk levels in a figure

#Plotting treatment/control stats on a bar plot
p_ec_risk <- ggplot(data = tc_stats_round) + 
  geom_col(aes(x = sample_type, y = `WHO 'High' Risk Contamination (> 100 MPN E. coli per 100 mL)`, fill = assignment), position = "dodge") +
  scale_y_continuous(
                     limits = c(0, 50),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% of samples")),
       fill = "Assignment",
       title = expression(paste("Proportion of Samples Considered 'High' Risk (> 100 MPN ", italic("E. coli"), " per 100 mL sample) Stratified by Round (N = 960)")),
       caption = "Stored and tap water samples were pooled across 5 monthly household surveys rounds across 20 villages in February, March, and April, July, and August 2024."
       )+
  facet_wrap(~ data_round)+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))



p_ec_risk


#Plotting stacked bar plot for risk levels

p_ec_risk_2 <- idexx_tab%>%
  filter(pooled_round == "FU")%>%
  ggplot(aes(x = assignment, fill = ec_risk)) +
  geom_bar(position = "fill", aes(y = ..prop.., group = ec_risk)) +
  facet_wrap(~ sample_type) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(
    values = c("High Risk" = "red", "Intermediate Risk" = "orange", "Low Risk" = "yellow", "Very Low Risk - Nondetectable" = "green"),
    name = expression(paste(italic("E. coli"), " Risk Level"))
  ) +
  labs(
    title = expression(paste("WHO ", italic("E. coli"),"Risk Classification Levels in Stored and Tap Drinking Water", " (0, 1-10, 10-100, >100 MPN ", italic("E. coli"),  " per 100 mL sample) (N = 961)")),
    x = "Study Assignment",
    y = "Proportion (%)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "right"
  )

p_ec_risk_2


ggsave(filename = "SI_ecoli_risk_levels_v1.jpeg", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 7, height = 3, units = "in", scale = 2)





#Displaying desc stats table for IDEXX

tc_stats_round%>%
  select(-c(`Lower CI - TC`, `Upper CI - TC`, `Lower CI - EC`, `Upper CI - EC`))%>%
kbl(caption = paste(
"IDEXX results stratified by data round")
)%>%
  kable_styling(
    full_width = FALSE,
  font_size = 7,                  # Adjust font size
  position = "center",             # Center the table
  latex_options = c("striped", "hold_position"), # Add stripes and prevent floating
  stripe_color = "gray!10",        # Set stripe color for readability
)%>%
  column_spec(1, bold = TRUE)


tc_stats_round%>%
  select(c(assignment, data_round, `Number of Samples`, `Tap - Average Free Chlorine Concentration (mg/L)`, `Stored - Average Free Chlorine Concentration (mg/L)`))%>%
kbl(caption = paste(
"IDEXX results stratified by data round")
)%>%
  kable_styling(
    full_width = FALSE,
  font_size = 7,                  # Adjust font size
  position = "center",             # Center the table
  latex_options = c("striped", "hold_position"), # Add stripes and prevent floating
  stripe_color = "gray!10",        # Set stripe color for readability
)%>%
  column_spec(1, bold = TRUE)




# (not including the stratification variable)
# library(tableone)
# my.vars <- c("Number of Samples", "% Positive for Total Coliform", "% Positive for E. coli"     , "Tap - Average Free Chlorine Concentration (mg/L)", "Stored - Average Free Chlorine Concentration (mg/L)")
# # create a list of which ones are categorical (factor)
# my.fvars <- c()
# 
# table.1 <- CreateTableOne(
# vars = my.vars,
# strata = c("data_round", "assignment", "sample_type"),
# data = tc_stats_round,
# includeNA = TRUE,
# test = FALSE,
# addOverall = TRUE) # No p-values in Table 1!
#  
# print(table.1) # Standard output
# 
# kable(
#   print(table.1,
#         showAllLevels = TRUE,
#         printToggle = FALSE,
#         noSpaces = TRUE,
#         catDigits = 1,
#         contDigits = 1),
#   caption = paste(
# "IDEXX Results Stratified by Round."),
# )%>%
#   kable_styling(
#     full_width = FALSE,
#   font_size = 7,                  # Adjust font size
#   position = "center",             # Center the table
#   latex_options = c("striped", "hold_position"), # Add stripes and prevent floating
#   stripe_color = "gray!10",        # Set stripe color for readability
# )%>%
#   column_spec(1, bold = TRUE)



#Desc stats -------------------

#Pooled Results
# fu_rounds <- all_rounds%>%
#   filter(data_round != "BL")#%>%
  #filter(available_jjm == "Both stored and running water are from JJM") #Removing chlorine data that are not from JJM source

fu_rounds <- all_rounds%>%
  filter(data_round != "BL")%>%
  filter(village != "Karnapadu")

#Making desc stat table for summarizing chlorine results from followup

# #Summarizing desc stats for positive results only
# desc_stats_tap <- fu_rounds%>%
#   filter(fc_tap_binary == 1 | tc_tap_binary == 1)%>%
#   group_by(assignment)%>%
#   summarise(
#     "Number of Samples" = n(),
#     "Tap - Average Free Chlorine Concentration (mg/L)" = mean(fc_tap_avg, na.rm = TRUE),
#     "Tap - Average Total Chlorine Concentration (mg/L)" = mean(tc_tap_avg, na.rm = TRUE),
#     "Tap - Free Chlorine - SD" = sd(fc_tap_avg, na.rm = TRUE),
#     "Tap - Total Chlorine - SD" = sd(tc_tap_avg, na.rm = TRUE)
#     )
# 
# 
# kbl(desc_stats_tap)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("Follow-up -- Average Chlorine Concentrations " = 6)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")
# 
# 
# desc_stats_stored <- fu_rounds%>%
#   filter(fc_stored_binary == 1 | tc_stored_binary == 1)%>%
#   group_by(assignment)%>%
#   summarise(
#     "Number of Samples" = n(),
#     "Stored - Average Free Chlorine Concentration (mg/L)" = mean(fc_stored_avg, na.rm = TRUE),
#     "Stored - Average Total Chlorine Concentration (mg/L)" = mean(tc_stored_avg, na.rm = TRUE),
#     "Stored - Free Chlorine - SD" = sd(fc_stored_avg, na.rm = TRUE),
#     "Stored - Total Chlorine - SD" = sd(tc_stored_avg, na.rm = TRUE)
#     )
# 
# kbl(desc_stats_stored)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("Follow-up -- Average Chlorine Concentrations " = 6)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")


#Chlorine Concentration-------------------------------------------------------

#Making desc stat table for summarizing chlorine results from followup
#Summarizing presence absence results after removing non-JJM samples
desc_stats_tap <- fu_rounds%>%
  group_by(assignment, data_round)%>%
  summarise(
    "Number of Samples" = n(),
    "Tap - Free Chlorine Presence" = mean(fc_tap_binary, na.rm = TRUE),
    "Tap - Total Chlorine Presence" = mean(tc_tap_binary, na.rm = TRUE),
    "Tap - Free Chlorine - SD" = sd(fc_tap_binary, na.rm = TRUE),
    "Tap - Total Chlorine - SD" = sd(tc_tap_binary, na.rm = TRUE)
    )


kbl(desc_stats_tap)%>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
  add_header_above(c("Follow-up -- Average Chlorine Concentrations " = 7)) %>%
  row_spec(0, bold = TRUE, color = "black", background = "white") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, width = "75px")


desc_stats_stored <- fu_rounds%>%
  group_by(assignment, data_round)%>%
  summarise(
    "Number of Samples" = n(),
    "Stored - Free Chlorine Presence" = mean(fc_stored_binary, na.rm = TRUE),
    "Stored - Total Chlorine Presence" = mean(tc_stored_binary, na.rm = TRUE),
    "Stored - Free Chlorine - SD" = sd(fc_stored_binary, na.rm = TRUE),
    "Stored - Total Chlorine - SD" = sd(tc_stored_binary, na.rm = TRUE)
    )

kbl(desc_stats_stored)%>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
  add_header_above(c("Follow-up -- Average Chlorine Concentrations " = 7)) %>%
  row_spec(0, bold = TRUE, color = "black", background = "white") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, width = "75px")

desc_stats_cl <- left_join(desc_stats_tap, desc_stats_stored, by = c("assignment", "data_round"))

kbl(desc_stats_cl)%>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
  add_header_above(c("Follow-up -- Average Chlorine Concentrations " = 12)) %>%
  row_spec(0, bold = TRUE, color = "black", background = "white") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, width = "75px")

#Comparing Chlorine Concentrations to E. coli contamination--------------

  
#Comparing IDEXX results to average chlorine concentration
idexx_tab <- idexx_tab%>%
  mutate(fc_tap_pa_2 = case_when(fc_tap_avg >= 0.2 ~ ">= 0.2 mg/L",
                                  fc_tap_avg < 0.2 ~ "< 0.2 mg/L"))%>%
  mutate(fc_stored_pa_2 = case_when(fc_stored_avg >= 0.2 ~ ">= 0.2 mg/L",
                                  fc_stored_avg < 0.2 ~ "< 0.2 mg/L"))%>%
  mutate(fc_tap_pa_1 = case_when(fc_tap_avg >= 0.1 ~ ">= 0.1 mg/L",
                                  fc_tap_avg < 0.1 ~ "< 0.1 mg/L"))%>%
  mutate(fc_stored_pa_1 = case_when(fc_stored_avg >= 0.1 ~ ">= 0.1 mg/L",
                                  fc_stored_avg < 0.1 ~ "< 0.1 mg/L"))%>%
  mutate(fc_ec_tap = case_when(fc_tap_avg >= 0.2 & ec_pa_binary == 0 ~ ">= 0.2 mg/L and absence of E. coli",
                                  fc_tap_avg >= 0.2 & ec_pa_binary == 1 ~ ">= 0.2 mg/L and presence of E. coli",
                               fc_tap_avg < 0.2 & ec_pa_binary == 0 ~ "< 0.2 mg/L and absence of E. coli",
                               fc_tap_avg < 0.2 & ec_pa_binary == 1 ~ "< 0.2 mg/L and presence of E. coli"
  ))
                          
                               
#Starting with tap results
tap_stats_pooled <- idexx_tab%>%
  filter(data_round != "BL")%>%
  filter(sample_type == "Tap")%>%
    group_by(fc_tap_pa_2) %>%
    summarise(
      "Number of Samples" = n(),
      "% Positive for Total Coliform" = round((sum(cf_pa == "Presence") / n()) * 100, 1),
      "% Positive for E. coli" = round((sum(ec_pa == "Presence") / n()) * 100, 1),
      "Lower CI - EC" = (sum(ec_pa == "Presence") / n()) * 100 -
        (qt(0.975, n() - 1) * sd(ec_pa_binary*100)/sqrt(n())),
      "Upper CI - EC" = (sum(ec_pa == "Presence") / n()) * 100 +
        (qt(0.975, n() - 1) * sd(ec_pa_binary*100)/sqrt(n())),
      # "Lower CI - EC" = {
      #   model <- glm(ec_pa_binary ~ 1, family = binomial)
      #   vcov_cluster <- vcovCR(model, cluster = village, type = "CR2")
      #   se <- sqrt(vcov_cluster[1, 1])
      #   est <- (sum(ec_pa == "Presence") / n()) * 100
      #   est - qt(0.975, df.residual(model)) * se
      # },
      # "Upper CI - EC" = {
      #   model <- glm(ec_pa_binary ~ 1, family = binomial)
      #   vcov_cluster <- vcovCR(model, cluster = village, type = "CR2")
      #   se <- sqrt(vcov_cluster[1, 1])
      #   est <- (sum(ec_pa == "Presence") / n()) * 100
      #   est + qt(0.975, df.residual(model)) * se
      # },
      "% Tap Samples with Free Chlorine > 0.2 mg/L" = 
        round((sum(fc_tap_pa_2 == "Presence") / n()) * 100, 1),
      "% Stored Samples with Free Chlorine > 0.2 mg/L" = 
        round((sum(fc_stored_pa_2 == "Presence") / n()) * 100, 1)
      )%>%
  rename(fc_level = "fc_tap_pa_2")%>%
  mutate(sample_type = "Tap")%>%
  mutate(`Lower CI - EC` = case_when(`Lower CI - EC` < 0 ~ 0,
                                       `Lower CI - EC` >= 0 ~ `Lower CI - EC`))%>%
    mutate(`Upper CI - EC` = case_when(`Upper CI - EC` > 100 ~ 100,
                                       `Upper CI - EC` <= 100 ~ `Upper CI - EC`))

stored_stats_pooled <- idexx_tab%>%
  filter(data_round != "BL")%>%
  filter(sample_type == "Stored")%>%
    group_by(fc_stored_pa_2) %>%
    summarise(
      "Number of Samples" = n(),
      "% Positive for Total Coliform" = round((sum(cf_pa == "Presence") / n()) * 100, 1),
      "% Positive for E. coli" = round((sum(ec_pa == "Presence") / n()) * 100, 1),
      "Lower CI - EC" = (sum(ec_pa == "Presence") / n()) * 100 -
        (qt(0.975, n() - 1) * sd(ec_pa_binary*100)/sqrt(n())),
      "Upper CI - EC" = (sum(ec_pa == "Presence") / n()) * 100 +
        (qt(0.975, n() - 1) * sd(ec_pa_binary*100)/sqrt(n())),
      # "Lower CI - EC" = {
      #   model <- glm(ec_pa_binary ~ 1, family = binomial)
      #   vcov_cluster <- vcovCR(model, cluster = village, type = "CR2")
      #   se <- sqrt(vcov_cluster[1, 1])
      #   est <- (sum(ec_pa == "Presence") / n()) * 100
      #   est - qt(0.975, df.residual(model)) * se
      # },
      # "Upper CI - EC" = {
      #   model <- glm(ec_pa_binary ~ 1, family = binomial)
      #   vcov_cluster <- vcovCR(model, cluster = village, type = "CR2")
      #   se <- sqrt(vcov_cluster[1, 1])
      #   est <- (sum(ec_pa == "Presence") / n()) * 100
      #   est + qt(0.975, df.residual(model)) * se
      # },
      "% Tap Samples with Free Chlorine > 0.2 mg/L" = 
        round((sum(fc_tap_pa_2 == "Presence") / n()) * 100, 1),
      "% Stored Samples with Free Chlorine > 0.2 mg/L" = 
        round((sum(fc_stored_pa_2 == "Presence") / n()) * 100, 1)
      )%>%
  rename(fc_level = "fc_stored_pa_2")%>%
  mutate(sample_type = "Stored")%>%
    #Adjusting so the CI cannot be more or less than 0 or 100
    mutate(`Lower CI - EC` = case_when(`Lower CI - EC` < 0 ~ 0,
                                       `Lower CI - EC` >= 0 ~ `Lower CI - EC`))%>%
    mutate(`Upper CI - EC` = case_when(`Upper CI - EC` > 100 ~ 100,
                                       `Upper CI - EC` <= 100 ~ `Upper CI - EC`))

cl_ec_plot_stats <- rbind(tap_stats_pooled, stored_stats_pooled)

#Making plot to display chlorine results vs IDEXX results

#new code
#Plotting treatment/control stats on a bar plot
p_cl_ec_pooled <- ggplot(data = cl_ec_plot_stats) + 
  geom_point(aes(x = sample_type, y = `% Positive for E. coli`, color = fc_level), 
           position = position_dodge(width = 0.35), size = 3) +
   geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     color = fc_level), position = position_dodge(width = 0.35),
                 width = .1) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       color = "Free Chlorine Concentration",
       title = expression(paste("Presence of ", italic("E. coli"), " in Drinking Water (N = 961)"))
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_classic() + 
  theme(axis.text.x = element_text(vjust=1))

p_cl_ec_pooled

ggsave(filename = "manuscript_cl_ecoli_comparison.pdf", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 2.5, height = 1.5, units = "in", scale = 2)


#----
# 
# p_tap_pooled <- ggplot(data = tap_stats_pooled) + 
#   geom_col(aes(x = fc_tap_pa_2, y = `% Positive for E. coli`), position = "dodge") +
#    geom_text(aes(x = fc_tap_pa_2, y = `% Positive for E. coli`,
#                 label = paste0(round(`% Positive for E. coli`, 1), "%")),
#             position = position_dodge(width = 0.9), vjust = -0.5) +
#   scale_y_continuous(
#                      limits = c(0, 100),
#                      expand = c(0,0))+
#   labs(x = "Free Chlorine Concentration (mg/L)", 
#        y = expression(paste("% positive for ",italic("E. coli"))),
#        title = "Tap Water",
#        caption = ""
#        #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
#        )+
#   theme_bw()
# 
# 
# 
# stored_stats_pooled <- idexx_tab%>%
#   filter(sample_type == "Stored")%>%
#     group_by(fc_stored_pa_2) %>%
#     summarise(
#       "Number of Samples" = n(),
#       "% Positive for Total Coliform" = round((sum(cf_pa == "Presence") / n()) * 100, 1),
#       "% Positive for E. coli" = round((sum(ec_pa == "Presence") / n()) * 100, 1),
#       "% Tap Samples with Free Chlorine > 0.2 mg/L" = 
#         round((sum(fc_tap_pa_2 == "Presence") / n()) * 100, 1),
#       "% Stored Samples with Free Chlorine > 0.2 mg/L" = 
#         round((sum(fc_stored_pa_2 == "Presence") / n()) * 100, 1)
#       )





#Making plot to display chlorine results vs IDEXX results

p_stored_pooled <- ggplot(data = stored_stats_pooled) + 
  geom_col(aes(x = fc_stored_pa_2, y = `% Positive for E. coli`), position = "dodge") +
  geom_text(aes(x = fc_stored_pa_2, y = `% Positive for E. coli`,
                label = paste0(round(`% Positive for E. coli`, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Free Chlorine Concentration (mg/L)", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       title = "Stored Water",
       caption = ""
       )+
  theme_bw()


#Patchwork package addition
p_pooled <- 
  p_tap_pooled + p_stored_pooled +
  plot_annotation(
  title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water vs Chlorine Concentration (N = 961)")),
  caption = "Stored and tap water samples were pooled across 6 household surveys rounds across 20 villages in February, March, April, August, September, and October 2024."
)

p_pooled

ggsave(filename = "SI_water_cl_comparison_v1.jpeg", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 6, height = 3, units = "in", scale = 2)






#Plotting time series data of microbial contamination and chlorine testing

#combining summary IDEXX data with weekly chlorine monitoring

idexx_cl_comb_1 <- mon_summary_weekly%>%
  select(test_week, avg_concentration, lower_ci, upper_ci, cl_presence, lower_ci_pa, upper_ci_pa)%>% #Selecting key variables
  mutate(sample_type = NA)%>%
  mutate(assignment = "Treatment")%>%
  mutate(`% Positive for E. coli` = NA)%>%
  mutate(`Lower CI - EC` = NA)%>%
  mutate(`Upper CI - EC` = NA)%>%
  mutate(`Lower CI - Tap` = NA) %>%
  mutate(`Upper CI - Tap` = NA)#Adding in variables from the other dataset so they can be directly combined


idexx_cl_comb_2 <- tc_stats_round%>%
  rename("test_week" = "data_round_month")%>% #renaming to align with other dataset
  select(test_week, assignment, sample_type, `% Positive for E. coli`,
         `Lower CI - EC`, `Upper CI - EC`, `Tap - Average Free Chlorine Concentration (mg/L)`,`Lower CI - Tap`, `Upper CI - Tap`)%>%
  filter(sample_type == "Tap")%>%
  mutate(
         lower_ci = NA,
         upper_ci = NA,
         cl_presence = NA,
         lower_ci_pa = NA,
         upper_ci_pa = NA)
idexx_cl_comb_2 <- idexx_cl_comb_2%>%
  rename("avg_concentration" = `Tap - Average Free Chlorine Concentration (mg/L)`)

#Removing chlorine tests from control group -- all null
idexx_cl_comb_2 <- idexx_cl_comb_2%>%
  mutate(avg_concentration = ifelse(avg_concentration > 0.05, avg_concentration, NA))%>%
  mutate(`Lower CI - Tap` = ifelse(avg_concentration > 0.05, `Lower CI - Tap`, NA))%>%
  mutate(`Upper CI - Tap` = ifelse(avg_concentration > 0.05, `Upper CI - Tap`, NA))


#Combining datasets together
idexx_cl_comb <- rbind(idexx_cl_comb_1, idexx_cl_comb_2)

#Creating scale value for figure
#scale_value <- max(idexx_cl_comb$`% Positive for E. coli`,
                    #na.rm = TRUE)/ max(idexx_cl_comb$avg_concentration, na.rm = TRUE)
scale_value <- 100/2


#Creating desc plot of weekly free chlorine results + IDEXX E. coli results

#Plotting treatment/control stats on a bar plot
p_ec_cl <- idexx_cl_comb%>%
  ggplot() + 
  geom_col(aes(x = test_week, y = `% Positive for E. coli`, fill = assignment), 
           position = "dodge", width = 12) +
   geom_errorbar(aes(x = test_week, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     fill = assignment), position = position_dodge(width = 12),
                 width = 6, color = "black") +
   geom_errorbar(aes(x = test_week, ymin = lower_ci*scale_value, ymax = upper_ci*scale_value),
                 width = 2, color = "#FF474C") + #Does not include robust standard errors for village clustering
  geom_point(aes(x = test_week, y = avg_concentration*scale_value), color = "#FF474C")+
  geom_path(aes(x = test_week, y = avg_concentration*scale_value), color = "#FF474C")+
  geom_vline(aes(xintercept = ymd("2024-02-01")), lty = 2, color = "#FF474C")+ #Placing intervention start date
  geom_text(aes(x = ymd("2024-02-01"), y = 80, label = "Intervention Start"), size = 3,
            nudge_x = -20, color = "#FF474C")+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0),
                     sec.axis = sec_axis(~./scale_value,
                                          name = 'Average Free Chlorine Concentration (mg/L)',
                                          breaks = c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2,
                                                     1.4, 1.6, 1.8, 2.0))
                     )+
  scale_x_date(
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
  scale_fill_brewer(palette = "Pastel1")+
  labs(x = "Date", 
       y = expression(paste("% tap samples positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))


p_ec_cl

ggsave(filename = "manuscript_ecoli_chlorine_time_series.jpeg", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 6, height = 3, units = "in", scale = 2)


#Creating plot to display the average chlorine concentrations along with the % of positive chlorine samples over time
p_cl <- mon_summary_weekly%>%
  ggplot() + 
  geom_col(aes(x = test_week, y = cl_presence), width = 12) +
   # geom_errorbar(aes(x = test_week, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
   #                   fill = assignment), position = position_dodge(width = 12),
                 #width = 6, color = "black") +
   geom_errorbar(aes(x = test_week, ymin = lower_ci*scale_value, ymax = upper_ci*scale_value),
                 width = 2, color = "red") + #Does not include robust standard errors for village clustering
  geom_point(aes(x = test_week, y = avg_concentration*scale_value), color = "red")+
  geom_path(aes(x = test_week, y = avg_concentration*scale_value), color = "red")+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0),
                     sec.axis = sec_axis(~./scale_value,
                                          name = 'Free Chlorine Concentration (mg/L)',
                                          breaks = c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2,
                                                     1.4, 1.6, 1.8, 2.0))
                     )+
  scale_x_date(
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
  labs(x = "Date", 
       y = "% tap samples positive for free chlorine (> 0.1 mg/L)",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cl


#Creating desc plot of weekly free chlorine positive samples + IDEXX E. coli results

#Plotting treatment/control stats on a bar plot
p_ec_cl_2 <- idexx_cl_comb%>%
  ggplot() + 
  geom_col(aes(x = test_week, y = `% Positive for E. coli`, fill = assignment), 
           position = "dodge", width = 12) +
   geom_errorbar(aes(x = test_week, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     fill = assignment), position = position_dodge(width = 12),
                 width = 6, color = "black") +
   geom_errorbar(aes(x = test_week, ymin = lower_ci_pa, ymax = upper_ci_pa),
                 width = 2, color = "#FF474C") + #Does not include robust standard errors for village clustering
  geom_point(aes(x = test_week, y = cl_presence), color = "#FF474C", size = 3)+
  #geom_path(aes(x = test_week, y = cl_presence), color = "#FF474C")+ #Geom path makes the plot cluttered
  geom_vline(aes(xintercept = ymd("2024-02-01")), lty = 2, color = "#FF474C")+ #Placing intervention start date
  geom_text(aes(x = ymd("2024-02-01"), y = 80, label = "Intervention Start"),
            nudge_x = -25, color = "#FF474C")+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0),
                     sec.axis = sec_axis(~.,
                                          name = '% of tap samples positive for free chlorine (> 0.1 mg/L)',
                                          breaks = c(0, 25, 50, 75, 100))
                     )+
  scale_x_date(
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
  scale_fill_brewer(palette = "Pastel1")+
  labs(x = "Date", 
       y = expression(paste("% of tap samples positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))


p_ec_cl_2

ggsave(filename = "manuscript_ecoli_chlorine_time_series_v2.jpeg", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 6, height = 3, units = "in", scale = 2)




#Separate microbial contamination and chlorine results -----

#Microbial results
#Plotting treatment/control stats on a bar plot
p_ec_cl_3 <- idexx_cl_comb%>%
  ggplot() + 
  geom_point(aes(x = test_week, y = `% Positive for E. coli`, color = assignment), 
           position = position_dodge(width = 5), size = 3) +
   geom_errorbar(aes(x = test_week, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     color = assignment), position = position_dodge(width = 5),
                 width = 6) +
  geom_vline(aes(xintercept = ymd("2024-02-01")), lty = 2, color = "#FF474C")+ #Placing intervention start date
  geom_text(aes(x = ymd("2024-02-01"), y = 80, label = "Intervention Start"),
            nudge_x = -19, color = "#FF474C", size = 3)+
  geom_vline(aes(xintercept = ymd("2024-07-01")), lty = 2, color = "darkblue")+ #Placing monsoon start date
  geom_text(aes(x = ymd("2024-07-01"), y = 80, label = "Monsoon Onset"), size = 3,
            nudge_x = -18, color = "darkblue")+
  geom_vline(aes(xintercept = ymd("2024-08-20")), lty = 2, color = "darkgreen")+ #Placing target dose change date
  geom_text(aes(x = ymd("2024-08-20"), y = 80, label = "Target"), size = 3,
            nudge_x = -10, color = "darkgreen")+
  geom_text(aes(x = ymd("2024-08-20"), y = 75, label = "Dose"), size = 3,
            nudge_x = -10, color = "darkgreen")+
  geom_text(aes(x = ymd("2024-08-20"), y = 70, label = "Increase"), size = 3,
            nudge_x = -10, color = "darkgreen")+
  scale_y_continuous(
                     limits = c(0, 105),
                     expand = c(0,0)
                     )+
  scale_x_date(limits = c(ymd("2023-10-06"), ymd("2024-10-15")),
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
  scale_fill_brewer(palette = "Pastel1")+
  labs(x = "Date", 
       y = expression(paste("% of tap samples positive for ",italic("E. coli"))),
       color = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_classic() + 
  theme(#axis.text.x = element_text(angle=45, vjust=1, hjust=1)
    axis.text.x = element_blank(),
    axis.title.x = element_blank()
    )


p_ec_cl_3

#ggsave(filename = "manuscript_ecoli_time_series_v3.jpeg", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 6, height = 1.5, units = "in", scale = 2)






#Plotting chlorine positive samples time series
p_ec_cl_4 <- idexx_cl_comb%>%
  ggplot() + 
   geom_errorbar(aes(x = test_week, ymin = lower_ci_pa, ymax = upper_ci_pa),
                 width = 2, color = "black") + #Does not include robust standard errors for village clustering
  geom_point(aes(x = test_week, y = cl_presence), size = 3)+
  geom_path(aes(x = test_week, y = cl_presence), color = "black")+ #Geom path makes the plot cluttered
  geom_vline(aes(xintercept = ymd("2024-02-01")), lty = 2, color = "#FF474C")+ #Placing intervention start date
    geom_vline(aes(xintercept = ymd("2024-07-01")), lty = 2, color = "darkblue")+ #Placing monsoon start date
  geom_vline(aes(xintercept = ymd("2024-08-20")), lty = 2, color = "darkgreen")+ #Placing target dose change date
  # geom_text(aes(x = ymd("2024-02-01"), y = 80, label = "Intervention Start"),
  #           nudge_x = -25, color = "#FF474C")+
  scale_y_continuous(
                     limits = c(0, 105),
                     expand = c(0,0)
                     )+
  scale_x_date(limits = c(ymd("2023-10-03"), ymd("2024-10-15")),
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
  scale_fill_brewer(palette = "Pastel1")+
  labs(x = "Date", 
       y = '% of tap samples positive for chlorine (>0.1 mg/L)',
       color = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        plot.title = element_text(size = 2))


p_ec_cl_4

#ggsave(filename = "manuscript_chlorine_time_series_v4.jpeg", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 5, height = 2, units = "in", scale = 2)

#Combining in patchwork so the scales are correct
p_ec_cl <- p_ec_cl_3 / p_ec_cl_4
p_ec_cl

ggsave(filename = "manuscript_e_coli_chlorine_time_series_v5.pdf", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 6, height = 3, units = "in", scale = 2)




#Plotting treatment/control stats on a bar plot
# p_ec_cl_5 <- idexx_cl_comb_2%>%
#   ggplot() + 
#   geom_col(aes(x = test_week, y = `% Positive for E. coli`, fill = assignment), 
#            position = "dodge", width = 12) +
#    geom_errorbar(aes(x = test_week, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
#                      fill = assignment), position = position_dodge(width = 12),
#                  width = 6, color = "black") +
#    geom_errorbar(aes(x = test_week, ymin = lower_ci*scale_value, ymax = upper_ci*scale_value),
#                  width = 2, color = "#FF474C") + #Does not include robust standard errors for village clustering
#   geom_point(aes(x = test_week+7, y = avg_concentration*scale_value), color = "#FF474C")+
#   geom_errorbar(aes(x = test_week+7, ymin = `Lower CI - Tap`*scale_value,
#                     ymax = `Upper CI - Tap`*scale_value), width = 2, color =  "#FF474C") +
#   #geom_path(aes(x = test_week+6, y = avg_concentration*scale_value), color = "#FF474C")+
#   geom_vline(aes(xintercept = ymd("2024-02-01")), lty = 2, color = "#FF474C")+ #Placing intervention start date
#   geom_text(aes(x = ymd("2024-02-01"), y = 80, label = "Intervention Start"), size = 3,
#             nudge_x = -20, color = "#FF474C")+
#   scale_y_continuous(
#                      limits = c(0, 100),
#                      expand = c(0,0),
#                      sec.axis = sec_axis(~./scale_value,
#                                           name = 'Average Free Chlorine Concentration (mg/L)',
#                                           breaks = c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2,
#                                                      1.4, 1.6, 1.8, 2.0))
#                      )+
#   scale_x_date(
#         date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
#         date_labels = "%b")+
#   scale_fill_brewer(palette = "Pastel1")+
#   labs(x = "Date", 
#        y = expression(paste("% tap samples positive for ",italic("E. coli"))),
#        fill = "Assignment",
#        title = "",
#        caption = ""
#        #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
#        )+
#   theme_bw() + 
#   theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))
# 
# 
# p_ec_cl_5







#Plotting treatment/control stats on a bar plot
p_ec_cl_6 <- idexx_cl_comb_2%>%
  ggplot() + 
  geom_col(aes(x = test_week, y = `% Positive for E. coli`, fill = assignment), 
           position = "dodge", width = 12) +
   geom_errorbar(aes(x = test_week, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     fill = assignment), position = position_dodge(width = 12),
                 width = 6, color = "black") +
   geom_errorbar(aes(x = test_week, ymin = lower_ci*scale_value, ymax = upper_ci*scale_value),
                 width = 2, color = "#FF474C") + #Does not include robust standard errors for village clustering
  geom_label(aes(x = test_week+10, label = avg_concentration, y = 1.5), size = 2.5, color = "#FF474C")+
  #geom_path(aes(x = test_week+6, y = avg_concentration*scale_value), color = "#FF474C")+
  geom_vline(aes(xintercept = ymd("2024-02-01")), lty = 2, color = "#FF474C")+ #Placing intervention start date
  geom_text(aes(x = ymd("2024-02-01"), y = 80, label = "Intervention Start"), size = 3,
            nudge_x = -18, color = "#FF474C")+
  geom_vline(aes(xintercept = ymd("2024-07-01")), lty = 2, color = "darkblue")+ #Placing monsoon start date
  geom_text(aes(x = ymd("2024-07-01"), y = 80, label = "Monsoon Onset"), size = 3,
            nudge_x = -16, color = "darkblue")+
  geom_vline(aes(xintercept = ymd("2024-08-20")), lty = 2, color = "darkgreen")+ #Placing target dose change date
  geom_text(aes(x = ymd("2024-08-20"), y = 80, label = "Target"), size = 3,
            nudge_x = -8, color = "darkgreen")+
  geom_text(aes(x = ymd("2024-08-20"), y = 76, label = "Dose"), size = 3,
            nudge_x = -8, color = "darkgreen")+
  geom_text(aes(x = ymd("2024-08-20"), y = 73, label = "Increase"), size = 3,
            nudge_x = -8, color = "darkgreen")+
  #geom_text(aes(x = ymd("2024-02-01"), y = 6, label = "Avg. Conc. (mg/L)"), size = 2.5,
   #         nudge_x = 30, color = "#FF474C")+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0)
                     )+
  scale_x_date(
        date_breaks = "1 month",   # Adds more frequent x-axis breaks (monthly)
        date_labels = "%b")+
  scale_fill_brewer(palette = "Pastel1")+
  labs(x = "Date", 
       y = expression(paste("% tap samples positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))


p_ec_cl_6





```











\newpage
# Antibiotic Resistance Analyses

```{r abr analyses}

#

#Creating plot of baseline ABR results
tc_stats_abr <- abr_stats(idexx_abr)%>%
  filter(data_round == "BL")

#Plotting treatment/control stats on a bar plot
p_ec_abr <- ggplot(data = tc_stats_abr) + 
  geom_point(aes(x = sample_type, y = `% Positive for E. coli`, color = assignment), 
           position = position_dodge(width = 0.35), size = 3) +
   geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     color = assignment), position = position_dodge(width = 0.35),
                 width = .2) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ABR ",italic("E. coli"))),
       color = "Assignment",
       title = expression(paste("Presence of Antibiotic Resistant ", italic("E. coli"), " in Household Drinking Water (N = 243)"))
       )+
  #facet_wrap(~ data_round)+
  theme_classic() + 
  theme(axis.text.x = element_text(vjust=1))

# p_cf_abr <- ggplot(data = tc_stats_abr) + 
#   geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
#     geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
#                       fill = assignment), position = position_dodge(width = 0.9),
#                  width = 0.25) +
#   #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
#   scale_y_continuous(
#                      limits = c(0, 100),
#                      expand = c(0,0))+
#   labs(x = "Sample Type", 
#        y = expression(paste("% positive for ABR total coliform")),
#        fill = "Assignment",
#        title = "",
#        caption = ""
#        )+
#   facet_wrap(~ data_round)+
#   theme_bw() + 
#   theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

#Patchwork package addition
# p_abr <- 
#   p_cf_abr + p_ec_abr +
#   plot_annotation(
#   title = expression(paste("Presence of Antibiotic Resistant Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 388 so far)")),
#   caption = "Stored and tap water samples were pooled across 2 monthly household surveys rounds across 20 villages in October 2023 and April 2024."
# )
# 
# p_abr
# 

p_ec_abr

#Creating total combined results
idexx_abr_fu <- idexx_abr%>%
  filter(data_round == "R3" | data_round == "R6")

tc_stats_abr_pooled <- pooled_stats_abr(idexx_abr_fu)

#Plotting treatment/control stats on a bar plot
p_ec_abr_pooled <- ggplot(data = tc_stats_abr_pooled) + 
  geom_point(aes(x = sample_type, y = `% Positive for E. coli`, color = assignment), 
           position = position_dodge(width = 0.35), size = 3) +
   geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                     color = assignment), position = position_dodge(width = 0.35),
                 width = .2) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ABR ",italic("E. coli"))),
       color = "Assignment",
       title = expression(paste("Presence of Antibiotic Resistant ", italic("E. coli"), " in Household Drinking Water (N = 243)"))
       )+
  #facet_wrap(~ data_round)+
  theme_classic() + 
  theme(axis.text.x = element_text(vjust=1))

p_ec_abr_pooled


p_abr <- p_ec_abr + p_ec_abr_pooled
p_abr

ggsave(filename = "manuscript_ABR_results.pdf", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 3.5, height = 1.5, units = "in", scale = 2)



# Poisson Regression - Treatment Effect -------------------------------------------------

#Removing BL data
idexx_abr_fu <- idexx_abr%>%
  filter(data_round != "BL")

#Separating by tap and stored water
idexx_abr_tap <- idexx_abr_fu%>%
  filter(sample_type == "Tap")

idexx_abr_stored <- idexx_abr_fu%>%
  filter(sample_type == "Stored")
  

#Running Poisson Regression on Tap Samples ----


outcome_vars <- c("cf_pa_binary","ec_pa_binary") #Selecting outcome variables

idexx_model <- factormaker(idexx_abr_tap, outcome_vars) #Converting to numeric type

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_tap <- ilc_model_table_only(all_models)
idexx_poisson_tap <- idexx_poisson_tap%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_tap", "ec_tap"))%>%
  mutate(sample_type = "Tap")


#Running Poisson Regression on Stored Samples ----

outcome_vars <- c("cf_pa_binary","ec_pa_binary") #Selecting outcome variables

idexx_model <- factormaker(idexx_abr_stored, outcome_vars) #Converting to numeric type

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_stored <- ilc_model_table_only(all_models)
idexx_poisson_stored <- idexx_poisson_stored%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_stored", "ec_stored"))%>%
  mutate(sample_type = "Stored")


idexx_abr_poisson <- rbind(idexx_poisson_tap, idexx_poisson_stored)




#Displaying results in a forestplot -----

library(forestplot)


#Adjusting model values to specifically fit forestplot function -- forestplot requires these names
el_models_forestplot <- idexx_abr_poisson%>%
  mutate(mean = estimate)%>%
  mutate(estimate = as.character(round(estimate, 2)))%>%
  mutate(Lower_CI = round(Lower_CI, 1))%>%
  mutate(Upper_CI = round(Upper_CI, 1))%>%
  mutate(estimate = paste0(estimate, " (", Lower_CI, ", ", Upper_CI, ")"))%>%
  mutate(lower = Lower_CI)%>%
  mutate(upper = Upper_CI)%>%
  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))

#Changing model names
el_models_forestplot$model_name <- el_models_forestplot$model_name%>%
  factor()%>%
  fct_recode("Presence of Free Chlorine (>0.1 mg/L)" = "fc_tap_binary",
             "Presence of Free Chlorine (>0.1 mg/L)" = "fc_stored_binary",
              "Stored - Presence of Total Coliform"= "cf_stored",
              "Stored - Presence of E. coli"= "ec_stored",
              "Tap - Presence of Total Coliform"= "cf_tap",
              "Tap - Presence of E. coli"= "ec_tap"
             )

el_forestplot <- el_models_forestplot%>%
  filter(model_name != "Presence of Total Coliform at Taps" )%>%
  filter(model_name != "Presence of Total Coliform in Stored Water")%>%
  forestplot(labeltext = c(model_name, estimate, p_value, N),
             title = "Intervention Effect on Cefotaxime-resistant Total Coliform and E. coli",
             caption = "Prevalence ratios were estimated using Poisson regression with robust standard errors for village-level clustering. Models include fixed effects for block and Panchayat village status randomization.",
             clip = c(0, 2),
             xticks = c(0, 0.5, 1, 1.5, 2),
             fn.ci_norm = fpDrawCircleCI,
             vertices = TRUE,
             xlog = FALSE,
             txt_gp = fpTxtGp(
               label = gpar(fontsize = 10),       # Adjust label text size
               ticks = gpar(fontsize = 15),       # Adjust tick text size
               xlab = gpar(fontsize = 15)),
             boxsize = 0.1
             )%>%
  fp_add_lines(h_3 = gpar(lty = 1), 
               h_7 = gpar(lwd = 1, columns = 1:5, col = "black"))%>% 
  fp_set_style(box = "black",
               line = "black",
               summary = "black",
               align = "lrrr",
               hrz_lines = "black")%>% 
  fp_add_header(model_name = c("", "Outcome"),
                estimate = c("Prevalence Ratio", "(95% CI)")%>%
                  fp_align_center(),
                p_value = c("", "P-value")%>% 
                  fp_align_center(),
                N = c("", "N")%>%
                  fp_align_center()
                )%>%
  fp_decorate_graph(grid = structure(c(1), 
                              gp = gpar(lty = 2, col = "grey")))

print(el_forestplot)











```






\newpage
# Chlorine and Microbial Contamination Treatment Effect

```{r Chlorine and Microbial Contamination Treatment Effect}



# Poisson Regression - Treatment Effect -------------------------------------------------

#Removing BL data
idexx_fu <- idexx_tab%>%
  filter(data_round != "BL")

#Separating by tap and stored water
idexx_fu_tap <- idexx_fu%>%
  filter(sample_type == "Tap")

idexx_fu_stored <- idexx_fu%>%
  filter(sample_type == "Stored")
  

#Running Poisson Regression on Tap Samples ----


outcome_vars <- c("cf_pa_binary","ec_pa_binary") #Selecting outcome variables

idexx_model <- factormaker(idexx_fu_tap, outcome_vars) #Converting to numeric type

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_tap <- ilc_model_table_only(all_models)
idexx_poisson_tap <- idexx_poisson_tap%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_tap", "ec_tap"))%>%
  mutate(sample_type = "Tap")


#Running Poisson Regression on Stored Samples ----

outcome_vars <- c("cf_pa_binary","ec_pa_binary") #Selecting outcome variables

idexx_model <- factormaker(idexx_fu_stored, outcome_vars) #Converting to numeric type

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_stored <- ilc_model_table_only(all_models)
idexx_poisson_stored <- idexx_poisson_stored%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_stored", "ec_stored"))%>%
  mutate(sample_type = "Stored")


idexx_poisson <- rbind(idexx_poisson_tap, idexx_poisson_stored)



#Running Linear Regression on Log-transformed E. coli Counts -- Treatment Effect

#Running on Tap Samples ----


outcome_vars <- c("cf_log","ec_log") #Selecting outcome variables

idexx_model <- idexx_fu_tap #setting model dataset

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_lm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_lm_tap <- ilc_model_lm_table_only(all_models)
idexx_lm_tap <- idexx_lm_tap%>%
  mutate(model_name = ifelse(model_name == "cf_log", "cf_log", "ec_log"))%>%
  mutate(sample_type = "Tap")


#Running Poisson Regression on Stored Samples ----

outcome_vars <- c("cf_log","ec_log") #Selecting outcome variables

idexx_model <- idexx_fu_stored #setting model dataset

#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_lm(data = idexx_model, var)
                 }
                  )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_lm_stored <- ilc_model_lm_table_only(all_models)
idexx_lm_stored <- idexx_lm_stored%>%
  mutate(model_name = ifelse(model_name == "cf_log", "cf_log", "ec_log"))%>%
  mutate(sample_type = "Stored")


idexx_lm <- rbind(idexx_lm_tap, idexx_lm_stored)







#-----------------------------------------------------------------------------


#-----------------------------------------------------------------------------


# Chlorine Concentration -----------------------------------------------------


#Running regression models -----------------------------------------------

#Variables
outcome_vars <- c("fc_tap_binary", "fc_stored_binary")

fu_model <- factormaker(fu_rounds, outcome_vars)


#Running all models
#Poisson regression
all_models <- lapply(outcome_vars,
                     function(var){ #This functions "subsets" the ilc_glm function
                       ilc_glm(data = fu_model, var)
                     }
                       )

#linear regression
# all_models <- lapply(outcome_vars, 
#                      function(var){ #This functions "subsets" the ilc_glm function
#                        ilc_lm(data = fu_rounds, var)
#                      }
#                        )

#Assigning names to models
names(all_models) <- outcome_vars

#Making regression table output
cl_poisson <- ilc_model_table_only(all_models)
cl_poisson <- cl_poisson%>%
  mutate(model_name = ifelse(model_name == "fc_tap_binary", "fc_tap", "fc_stored"))%>%
  mutate(sample_type = ifelse(model_name == "fc_tap_binary", "Tap", "Stored"))


#Combining microbial contamination and chlorination treatment effect results
fu_poisson <- rbind(idexx_poisson, cl_poisson)


#Displaying results in a forestplot -----

library(forestplot)


#Adjusting model values to specifically fit forestplot function
el_models_forestplot <- fu_poisson%>%
  mutate(mean = estimate)%>%
  mutate(estimate = as.character(round(estimate, 2)))%>%
  mutate(Lower_CI = round(Lower_CI, 1))%>%
  mutate(Upper_CI = round(Upper_CI, 1))%>%
  mutate(estimate = paste0(estimate, " (", Lower_CI, ", ", Upper_CI, ")"))%>%
  mutate(lower = Lower_CI)%>%
  mutate(upper = Upper_CI)%>%
  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))

#Changing model names
el_models_forestplot$model_name <- el_models_forestplot$model_name%>%
  factor()%>%
  fct_recode("Presence of Free Chlorine at Taps (>0.1 mg/L)" = "fc_tap",
             "Presence of Free Chlorine in Stored Water (>0.1 mg/L)" = "fc_stored",
              "Presence of Total Coliform at Taps"= "cf_tap",
              "Presence of E. coli at Taps"= "ec_tap",
              "Presence of Total Coliform in Stored Water"= "cf_stored",
              "Presence of E. coli in Stored Water"= "ec_stored")

el_forestplot <- el_models_forestplot%>%
  forestplot(labeltext = c(model_name, estimate, p_value, N),
             title = "Intervention Effect on Microbiological Contamination and Chlorination",
             caption = "Prevalence ratios were estimated using Poisson regression with robust standard errors for village-level clustering. Models include fixed effects for block and Panchayat village status randomization.",
             clip = c(0, 2),
             xticks = c(0, 0.5, 1, 1.5, 2),
             fn.ci_norm = fpDrawCircleCI,
             vertices = TRUE,
             xlog = FALSE,
             txt_gp = fpTxtGp(
               label = gpar(fontsize = 10),       # Adjust label text size
               ticks = gpar(fontsize = 15),       # Adjust tick text size
               xlab = gpar(fontsize = 15)),
             boxsize = 0.2
             )%>%
  fp_add_lines(h_3 = gpar(lty = 1), 
               h_9 = gpar(lwd = 1, columns = 1:5, col = "black"))%>% 
  fp_set_style(box = "black",
               line = "black",
               summary = "black",
               align = "lrrr",
               hrz_lines = "black")%>% 
  fp_add_header(model_name = c("", "Outcome"),
                estimate = c("Prevalence Ratio", "(95% CI)")%>%
                  fp_align_center(),
                p_value = c("", "P-value")%>% 
                  fp_align_center(),
                N = c("", "N")%>%
                  fp_align_center()
                )%>%
  fp_decorate_graph(grid = structure(c(1), 
                              gp = gpar(lty = 2, col = "grey")))

print(el_forestplot)










```

#Endline Desc Stats

```{r Endline Desc Stats}

#Baseline Census Desc Stats
outcome_vars <- c("assignment",#"hhmember_count", "hhhead_gender", "read_write_1",
                  "prim_source", "sec_source","jjm_drinking", "water_treat_binary",
                   "time_spent_treat", "time_spent_treat_15", "tap_issues_taste"
                  )

#GT method
#Summarizing desc stats for each variable
#reset_gtsummary_theme()
desc_stats_el <- el%>%
  dplyr::select(all_of(outcome_vars))%>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(prim_source ~ "Primary drinking water source",
                                 sec_source ~ "Use a secondary drinking water source",
                                 jjm_drinking ~ "Drink water from their tap connection",
                                 water_treat_binary ~ "Treat drinking water",
                                 time_spent_treat ~ "Time spent treating water is > 10 minutes",
                                 time_spent_treat_15 ~ "Time spent treating water is > 15 minutes",
                                 tap_issues_taste ~ "Reported smell or taste issue from tap water"
                                 )
                    )%>%
  add_n()

desc_stats_el_gt <- as_tibble(desc_stats_el)%>%
  gt::gt()

# desc_stats_cen_gt%>%
#   gtsave(path = (paste0(github_path(), "/3_manuscript/figures")), filename = "desc_stats_cen.pdf")

desc_stats_el_df <- desc_stats_el%>%
  as.data.frame()%>%
  rename("Treatment" = `**Treatment**  \nN = 405`)%>%
  rename("Control" = `**Control**  \nN = 475`)






#Subsetting follow-up survey rounds
fu_rounds <- all_rounds%>%
  filter(data_round != "BL")

#Baseline followup survey desc stats
outcome_vars <- c("assignment", "fc_tap_binary", "fc_stored_binary",
                  "fc_tap_.2", "fc_stored_.2", "fc_tap_2ppm", "fc_stored_2ppm",
                  "tap_taste_binary"
                  )

desc_stats_fu <- fu_rounds%>%
  dplyr::select(all_of(outcome_vars))%>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(
                                 fc_tap_binary ~ "Presence of free chlorine at tap connection",
                                 fc_stored_binary ~ "Presence of free chlorine in stored water",
                                 fc_tap_.2 ~ "Proportion of samples > 0.2 mg/L at tap",
                                 fc_stored_.2 ~ "Proportion of samples > 0.2 mg/L in stored water",
                                 fc_tap_2ppm ~ "Proportion of samples > 2.0 mg/L at tap",
                                 fc_stored_2ppm ~ "Proportion of samples > 2.0 mg/L in stored water",
                                 tap_taste_binary ~ "Satisfied with taste of tap water"
                                 )
                    )%>%
  add_n()

desc_stats_fu_gt <- as_tibble(desc_stats_fu)%>%
  gt::gt()

# desc_stats_bl_gt%>%
#   gtsave(path = (paste0(github_path(), "/3_manuscript/figures")), filename = "desc_stats_bl.pdf")

desc_stats_fu_df <- desc_stats_fu%>%
  as.data.frame()%>%
  rename("Treatment" = `**Treatment**  \nN = 421`)%>%
  rename("Control" = `**Control**  \nN = 420`)


#Separating stored vs tap water tests ------

idexx_fu_tap <- idexx_fu%>%
  filter(sample_type == "Tap")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_tap = "cf_pa_binary")%>%
  rename(ec_pa_tap = "ec_pa_binary")%>%
  rename(cf_log_tap = "cf_log")%>%
  rename(ec_log_tap = "ec_log")

idexx_fu_stored <- idexx_fu%>%
  filter(sample_type == "Stored")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_stored = "cf_pa_binary")%>%
  rename(ec_pa_stored = "ec_pa_binary")%>%
  rename(cf_log_stored = "cf_log")%>%
  rename(ec_log_stored = "ec_log")



#Summarizing desc stats --------------------------------------

#Tap water
desc_stats_fu_tap <- idexx_fu_tap%>%
  dplyr::select(assignment, cf_pa_tap, ec_pa_tap, 
                cf_log_tap, ec_log_tap
                )%>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("cf_pa_tap", "ec_pa_tap",
                             "cf_log_tap","ec_log_tap"
                             ) ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(cf_pa_tap ~ "Tap - Presence/Absence of Total Coliform",
                                 ec_pa_tap ~ "Tap - Presence/Absence of E. coli",
                                 cf_log_tap ~ "Tap - Mean Log10 of Total Coliform",
                                 ec_log_tap ~ "Tap - Mean Log10 of E. coli"
                                )
                    )%>%
  add_n()%>%
  as.data.frame()%>%
  rename("Treatment" = `**Treatment**  \nN = 240`)%>%
  rename("Control" = `**Control**  \nN = 241`)


#Stored water
desc_stats_fu_stored <- idexx_fu_stored%>%
  dplyr::select(assignment, cf_pa_stored, ec_pa_stored, cf_log_stored, ec_log_stored
                )%>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("cf_pa_stored", "ec_pa_stored",
                             "cf_log_stored", "ec_log_stored"
                             ) ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(cf_pa_stored ~ "Stored - Presence/Absence of Total Coliform",
                                 ec_pa_stored ~ "Stored - Presence/Absence of E. coli",
                                 cf_log_stored ~ "Stored - Mean Log10 of Total Coliform",
                                 ec_log_stored ~ "Stored - Mean Log10 of E. coli"
                                )
                    )%>%
  add_n()%>%
  as.data.frame()%>%
  rename("Treatment" = `**Treatment**  \nN = 240`)%>%
  rename("Control" = `**Control**  \nN = 240`)


#Recombining tables
desc_stats_fu <- bind_rows(desc_stats_el_df, desc_stats_fu_df)%>% 
  bind_rows(desc_stats_fu_tap)%>%
  bind_rows(desc_stats_fu_stored)%>%
  as_tibble()%>%
  gt::gt()

desc_stats_fu%>%
  gtsave(path = (paste0(github_path(), "/3_manuscript/figures")), filename = "desc_stats_fu.pdf")






```


\newpage
# Endline Treatment Effect

```{r Endline Census Comparison}


#Desc Stats --------------------------------------------------

#Selecting variables
outcome_vars <- c("prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary", "time_spent_treat", "time_spent_treat_15")


#GT method
#Summarizing desc stats for each variable
desc_stats <- el%>%
  dplyr::select("assignment", "prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary", "time_spent_treat", "time_spent_treat_binary")%>%
  tbl_summary(
  by = assignment,
  statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} / {N} ({p}%)"),
  digits = all_continuous() ~ 2
)%>%
  add_p()



# Poisson Regression -- Treatment Effect -------------------------------------

outcome_vars <- c("prim_source_jjm", "sec_source",
                  "jjm_drinking", "water_treat_binary", "tap_issues_taste", "time_spent_treat", "time_spent_treat_15", "time_spent_treat_5")

el_model <- factormaker(el, outcome_vars) #Making variables numeric


#Poisson Regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = el_model, var)
                 }
                  )
#linear regression
# all_models <- lapply(outcome_vars, 
#                      function(var){ #This functions "subsets" the ilc_glm function
#                        ilc_lm(data = el_model, var)
#                      }
#                        )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
el_models <- ilc_model_table_only(all_models)
ilc_model_table(all_models)






# Combined Desc Stats - baseline and endline --------------------------------------------

#Selecting jjm variables
el_jjm <- el%>%
  dplyr::select(assignment, prim_source, water_sec_yn, jjm_drinking, tap_issues, tap_issues_type_1)%>%
  mutate(data_round = "Endline")

cen_jjm <- cen%>%
  dplyr::select(assignment, prim_source, water_sec_yn, jjm_drinking)%>%
  mutate(data_round = "Baseline")%>%
  mutate(tap_issues = NA)%>%
  mutate(tap_issues_type_1 = NA)
#Combining EL and BL datasets
total_jjm <- rbind(cen_jjm, el_jjm)



# #Summarizing combined results in a table
# tab <- total_jjm%>%
#   tbl_strata(
#     strata = data_round,
#     .tbl_fun =
#       ~ .x %>%
#         tbl_summary(by = assignment, 
#                     missing = "no", 
#                     #type = c() ~ "continuous",
#                     statistic = list(
#                       all_continuous() ~ "{mean} ({sd})",
#                       all_categorical() ~ "{p}% ({n})"),
#                     digits = list(all_continuous() ~ 2, 
#                                   all_categorical() ~ 0),
#                     label = list(prim_source ~ "Primary Drinking Water Source",
#                                  jjm_drinking ~ "Use Government-provided Tap for Drinking",
#                                  water_sec_yn ~ "Used a Secondary Drinking Water Source in Last Month",
#                                  tap_issues ~ "Issues with Government-provided Tap (2 weeks)",
#                                  tap_issues_type_1 ~ "Reported Taste/Odor/Cooking Issue"
#                                  )
#                     )%>%
#      modify_footnote(all_stat_cols() ~ "% (N); BL - Oct 2023, EL - May 2024"),#%>%
#  # as_gt()%>%
#   #tab_options(table.font.size = pct(50),
#               #table_body.hlines.width = 
#    #             table.width = pct(50)),
#     .header = "**{strata}**"
#   )
# 
# # Convert to gt object
# gt_tab <- as_gt(tab)
# 

```


```{r Endline census comparison forest plot}


# # create forest plot on log scale (middle section of figure)
# p_mid <- el_models%>%
#   ggplot(aes(y = model_name)) +
#   theme_classic() +
#   geom_point(aes(x=estimate), shape=15, size=3) +
#   geom_linerange(aes(xmin=Lower_CI, xmax=Upper_CI))+
#   labs(x="Prevalence Ratio") +
#   coord_cartesian(ylim=c(1,length(el_models$model_name)+1), xlim=c(0, 2))+
#   geom_vline(xintercept = 1, linetype="dashed") +
#   annotate("text", x = 0.3, y = length(el_models$model_name)+1, label = " ") +
#   annotate("text", x = 1.7, y = length(el_models$model_name)+1, label = " ") +
#   theme(axis.line.y = element_blank(),
#         axis.ticks.y= element_blank(),
#         axis.text.y= element_blank(),
#         axis.title.y= element_blank())
#   
# # wrangle results into pre-plotting table form
# res_plot <- el_models%>%
#   mutate(across(c(estimate, Lower_CI, Upper_CI), ~str_pad(round(.x, 2), width=3, pad=" ", side="right")),
#          estimate = paste0(estimate, " (", Lower_CI, ",", Upper_CI,")"),
#          color = rep(c("gray","white"), length(el_models$model_name)/2))%>%
#   mutate(p_value = case_when(p_value < .01 ~ "<0.01", TRUE ~ str_pad(as.character(round(p_value, 2)),width=4,pad="0",side="right")))%>%
#   bind_rows(data.frame(model_name = "Covariate", estimate = "Prevalence Ratio (95% CI)", Lower_CI = "", Upper_CI="",p_value="p-value"))%>%
#   mutate(model_name = fct_rev(fct_relevel(model_name, "Covariate")))
# 
# # left side of plot - prevalence ratios
# p_left <-
#   res_plot%>%
#   ggplot(aes(y = model_name)) + 
#   geom_text(aes(x=0, label=model_name), hjust=0, fontface = "bold") +
#   geom_text(aes(x=2.2, label=estimate), hjust=0, fontface = ifelse(res_plot$estimate == "Prevalence Ratio (95% CI)", "bold", "plain")) +
#   theme_void() +
#   coord_cartesian(xlim=c(0,4))
# # right side of plot - pvalues
# p_right <-
#   res_plot%>%
#   ggplot() +
#   geom_text(aes(x=0, y=model_name, label=p_value), hjust=0, fontface = ifelse(res_plot$p_value == "p-value", "bold", "plain")) +
#   theme_void() 
# # layout design (top, left, bottom, right)
# layout <- c(
#   area(t = 0, l = 0, b = 30, r = 4),
#   area(t = 1, l = 5, b = 30, r = 10),
#   area(t = 0, l = 10, b = 30, r = 12)
# )
# # final plot arrangement
# p_endline_results = p_left + p_mid + p_right + plot_layout(design = layout)
# 
# p_endline_results
# 
# 

#Another forestplot method
#Unfortunately this package has depreciated
library(forestplot)


#Adjusting model values to specifically fit forestplot function
el_models_forestplot <- el_models%>%
  mutate(mean = estimate)%>%
  mutate(estimate = as.character(round(estimate, 2)))%>%
  mutate(Lower_CI = round(Lower_CI, 2))%>%
  mutate(Upper_CI = round(Upper_CI, 2))%>%
  mutate(estimate = paste0(estimate, " (", Lower_CI, ", ", Upper_CI, ")"))%>%
  mutate(lower = Lower_CI)%>%
  mutate(upper = Upper_CI)%>%
  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))

#Changing model names
el_models_forestplot$model_name <- el_models_forestplot$model_name%>%
  factor()%>%
  fct_recode("Taps as Primary Source" = "prim_source_jjm",
             "Use a Secondary Source" = "sec_source",
             "Drink Tap Water" = "jjm_drinking",
             "Treat Water" = "water_treat_binary",
             "Reported Water Taste/Smell Issue" = "tap_issues_taste",
             "Time Spent Treating Water is >10 minutes" = "time_spent_treat")

el_forestplot <- el_models_forestplot%>%
  forestplot(labeltext = c(model_name, estimate, p_value),
             title = "Intervention Effect on WASH Outcomes (N = 875)",
             caption = "Prevalence ratios were estimated using Poisson regression with robust standard errors for village-level clustering. Models include fixed effects for block and Panchayat village status randomization.",
             clip = c(0, 2),
             xticks = c(0, 0.5, 1, 1.5, 2),
             fn.ci_norm = fpDrawCircleCI,
             vertices = TRUE,
             xlog = FALSE,
             txt_gp = fpTxtGp(
               label = gpar(fontsize = 10),       # Adjust label text size
               ticks = gpar(fontsize = 15),       # Adjust tick text size
               xlab = gpar(fontsize = 15)),
             boxsize = 0.2
             )%>%
  fp_add_lines(h_3 = gpar(lty = 1), 
               h_9 = gpar(lwd = 1, columns = 1:4, col = "black"))%>% 
  fp_set_style(box = "black",
               line = "black",
               summary = "black",
               align = "lrrr",
               hrz_lines = "black")%>% 
  fp_add_header(model_name = c("", "Outcome"),
                estimate = c("Prevalence Ratio", "(95% CI)")%>%
                  fp_align_center(),
                p_value = c("", "P-value")%>% 
                  fp_align_center()
                )%>%
  fp_decorate_graph(grid = structure(c(1), 
                              gp = gpar(lty = 2, col = "grey")))

print(el_forestplot)


```



```{r endline -- trying to understand robust SE issues}



# formula <- as.formula(paste("jjm_drinking", "~ assignment + block + panchayat_village"))
#   #Running model
#   model <- glm(formula, data = el_model, family = poisson)
#   
#   #Storing N
#   N <- length(model$y)
#   
#   #Storing Standard Errors
#   #std_errors <- sqrt(diag(vcov(model)))
#   
#   #Calculating conf intervals
#   #conf_intervals <- exp(confint.default(model)) #This shows how my original estimation method was off!
#   
#   # Adjust for clustering at the village level
#   cluster_vcov <- vcovCL(model, cluster = el_model$village, type = "HC1")
#   # Get the coefficients with clustered standard errors
#   clustered_results <- coeftest(model, vcov. = cluster_vcov)
#   
#   #Tidying models -- need to understand how to use clustered results option
#   tidy_results <- tidy(clustered_results)
#   # Rename the columns for better readability
#   colnames(tidy_results) <- c("covariate", "estimate", "std_error", "z_statistic", "p_value")
#   
#   #Adding N
#   tidy_results <- tidy_results%>%
#     mutate(N = N)
#   
#   #exponentiate the estimates/std errors to get Prevalence Ratio
#   
#   tidy_results$estimate <- exp(tidy_results$estimate)
#   tidy_results$std_error <- exp(tidy_results$std_error)
#   
#   tidy_results

```

## Combined Microbial Contamination and Water Use Effects

```{r Full Forestplot results}


#combined regular and ABR IDEXX results

#Removed total coliform and e. coli tap results from ABR IDEXX
# idexx_abr_poisson <- idexx_abr_poisson%>%
#   filter(model_name != "cf_tap")%>%
#   filter(model_name != "cf_stored")%>%
#   mutate(model_name = ifelse(model_name == "ec_stored","Presence Antibiotic Resistant E. coli in Stored Water", "Presence Antibiotic Resistant E. coli in Tap Water"))%>%
#   select(!(sample_type))
# 
# 
# #Removing chlorine results from regular IDEXX results
# fu_poisson <- fu_poisson%>%
#   filter(model_name != "fc_tap")%>%
#   filter(model_name != "fc_stored")%>%
#   select(!(sample_type))
# 
# #Joining poisson results
# el_models_forestplot <- rbind(fu_poisson, idexx_abr_poisson, el_models)
# 
# 
# #Changing model names
# el_models_forestplot <- el_models_forestplot%>%
#   mutate(mean = estimate)%>%
#   mutate(estimate = as.character(round(estimate, 2)))%>%
#   mutate(Lower_CI = round(Lower_CI, 2))%>%
#   mutate(Upper_CI = round(Upper_CI, 2))%>%
#   mutate(estimate = paste0(estimate, " (", Lower_CI, ", ", Upper_CI, ")"))%>%
#   mutate(lower = Lower_CI)%>%
#   mutate(upper = Upper_CI)%>%
#   mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))
# 
# el_models_forestplot$model_name <- el_models_forestplot$model_name%>%
#   factor()%>%
#   fct_recode("Presence of Total Coliform at Taps"= "cf_tap",
#               "Presence of E. coli at Taps"= "ec_tap",
#               "Presence of Total Coliform in Stored Water"= "cf_stored",
#               "Presence of E. coli in Stored Water"= "ec_stored",
#              "Presence Antibiotic Resistant E. coli in Stored Water" =
#                "Presence Antibiotic Resistant E. coli in Stored Water",
#              "Taps as Primary Source" = "prim_source_jjm",
#              "Use a Secondary Source" = "sec_source",
#              "Drink Tap Water" = "jjm_drinking",
#              "Treat Water" = "water_treat_binary",
#              "Reported Water Taste/Smell Issue" = "tap_issues_taste",
#              "Time Spent Treating Water is >10 Minutes" = "time_spent_treat"
#              )
# 
# el_forestplot <- el_models_forestplot%>%
#   forestplot(labeltext = c(model_name, estimate, p_value, N),
#              title = "Intervention Effect on Key Water Use and Quality Outcomes",
#              caption = "Prevalence ratios were estimated using Poisson regression with robust standard errors for village-level clustering. Models include fixed effects for block and Panchayat village status randomization.",
#              clip = c(0, 1.5),
#              xticks = c(0, 0.5, 1, 1.5),
#              fn.ci_norm = fpDrawCircleCI,
#              vertices = TRUE,
#              xlog = FALSE,
#              txt_gp = fpTxtGp(
#                label = gpar(fontsize = 10),       # Adjust label text size
#                ticks = gpar(fontsize = 15),       # Adjust tick text size
#                xlab = gpar(fontsize = 15)),
#              boxsize = 0.2
#              )%>%
#   fp_add_lines(h_3 = gpar(lty = 1), 
#                h_15 = gpar(lwd = 1, columns = 1:5, col = "black"))%>% 
#   fp_set_style(box = "black",
#                line = "black",
#                summary = "black",
#                align = "lrrr",
#                hrz_lines = "black")%>% 
#   fp_add_header(model_name = c("", "Outcome"),
#                 estimate = c("Prevalence Ratio", "(95% CI)")%>%
#                   fp_align_center(),
#                 p_value = c("", "P-value")%>% 
#                   fp_align_center(),
#                 N = c("", "N")%>%
#                   fp_align_center()
#                 )%>%
#   fp_decorate_graph(grid = structure(c(1), 
#                               gp = gpar(lty = 2, col = "grey")))
# 
print(el_forestplot)






```




# Combined Forestplot Using ggplot


```{r ggplot forestplot}

####Code provided by Courtney Victor, UNC W&H Conference 2024


#Removed total coliform and e. coli tap results from ABR IDEXX
idexx_abr_poisson <- idexx_abr_poisson%>%
  filter(model_name != "cf_tap")%>%
  filter(model_name != "cf_stored")%>%
  mutate(model_name = ifelse(model_name == "ec_stored","Presence Antibiotic Resistant E. coli in Stored Water", "Presence Antibiotic Resistant E. coli in Tap Water"))%>%
  select(!(sample_type))


#Removing chlorine results from regular IDEXX results
fu_poisson <- fu_poisson%>%
  filter(model_name != "fc_tap")%>%
  filter(model_name != "fc_stored")%>%
  select(!(sample_type))

#Joining poisson results
el_models_forestplot <- rbind(fu_poisson, idexx_abr_poisson, el_models)

#Setting order of variables
#Changing model names
el_models_forestplot <- el_models_forestplot%>%
  mutate(mean = estimate)%>%
  mutate(estimate = as.character(round(estimate, 2)))%>%
  mutate(Lower_CI = round(Lower_CI, 2))%>%
  mutate(Upper_CI = round(Upper_CI, 2))%>%
  mutate(estimate = paste0(estimate, " (", Lower_CI, ", ", Upper_CI, ")"))%>%
  mutate(lower = Lower_CI)%>%
  mutate(upper = Upper_CI)%>%
  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))




el_models_forestplot$model_name <- el_models_forestplot$model_name%>%
  factor()%>%
  fct_recode("Presence of Total Coliform at Taps"= "cf_tap",
              "Presence of E. coli at Taps"= "ec_tap",
              "Presence of Total Coliform in Stored Water"= "cf_stored",
              "Presence of E. coli in Stored Water"= "ec_stored",
             "Presence Antibiotic Resistant E. coli in Stored Water" =
              "Presence Antibiotic Resistant E. coli in Stored Water",
             "Taps as Primary Source" = "prim_source_jjm",
             "Use a Secondary Source" = "sec_source",
             "Drink Tap Water" = "jjm_drinking",
             "Treat Water" = "water_treat_binary",
             "Reported Water Taste/Smell Issue" = "tap_issues_taste",
             "Time Spent Treating Water is >10 Minutes" = "time_spent_treat"
             )
#Reordering
el_models_forestplot$model_name <- factor(el_models_forestplot$model_name, levels = 
                                            c(
             "Time Spent Treating Water is >10 Minutes",
             "Reported Water Taste/Smell Issue",
             "Treat Water",
             "Drink Tap Water",
              "Use a Secondary Source",
             "Taps as Primary Source",
             "Presence Antibiotic Resistant E. coli in Stored Water",
              "Presence Antibiotic Resistant E. coli in Tap Water",
             "Presence of E. coli in Stored Water",
             "Presence of Total Coliform in Stored Water",
             "Presence of E. coli at Taps",
             "Presence of Total Coliform at Taps"
             ))

el_models_forestplot <- el_models_forestplot%>%
  mutate(variable_type = ifelse(model_name %in% c("Presence Antibiotic Resistant E. coli in Stored Water",
              "Presence Antibiotic Resistant E. coli in Tap Water",
             "Presence of E. coli in Stored Water",
             "Presence of Total Coliform in Stored Water",
             "Presence of E. coli at Taps",
             "Presence of Total Coliform at Taps"), "Water Quality Outcome", "Behavioral Outcome"))


#Manually adding in column names to the figure
# el_models_forestplot <- el_models_forestplot%>%
#   bind_rows(
#     data.frame(
#       model_name = "Outcome",
#       covariate = NA,
#       estimate = "Prevalence Ratio (95% CI)",
#       std_error = NA,
#       p_value = "P-value",
#       N = NA,
#       Lower_CI = NA,
#       Upper_CI = NA,
#       signif = NA,
#       mean = NA,
#       lower = NA,
#       upper = NA
#     ))
#This is not a good option


#Creating Foresplot using ggplot

## Create plot 
p_forestplot <- ggplot(el_models_forestplot, aes(x = mean, y = model_name)) +
  geom_point(aes(color = variable_type), size = 2) +  
  geom_errorbarh(aes(xmin = Lower_CI, xmax = Upper_CI,  color = variable_type), height = 0.2) + 
  geom_vline(xintercept = 1, linetype = "dashed", color = "black") +# Dashed line at x = 1 (null Risk Ratio)
  scale_y_discrete(labels = function(y) str_wrap(y, width = 35)) +
  scale_x_continuous(limits = c(0.5, 1.90), breaks = c(0.50, 0.75, 1.00, 1.2))+
  scale_color_manual(values = c("Water Quality Outcome" = "#00008B", "Behavioral Outcome" = "#EEA944"))
  labs(
    x = "Prevalence Ratio", 
    y = "Outcome") + 
  theme_classic() +
  theme(legend.title = element_blank(),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size = 13),
        axis.title.x = element_text(size = 13)) #+
  #guides(color = guide_legend(reverse = TRUE)) # Ensures the order of the legend matches the order in which point estimates appear on the plot

# Add horizontal lines between levels of outcomes to create separation
y_levels <- levels(factor(el_models_forestplot$model_name))
y_positions <- seq_along(y_levels) - 0.5
for (y in y_positions) {
  p_forestplot <- p_forestplot + geom_hline(yintercept = y, color = "darkgrey", linetype = "solid", linewidth = 0.5)
}

#Adding in effect estimates and p-values
p_forestplot <- p_forestplot + 
  geom_text(aes(label = estimate, x = max(Upper_CI) + 0.25), hjust = 0, size = 3) + 
    geom_text(aes(label = p_value, x = max(Upper_CI) + 0.50), hjust = 0, size = 3) + 
    geom_text(aes(label = N, x = max(Upper_CI) + 0.65), hjust = 0, size = 3)
  

#Viewing
p_forestplot

ggsave(filename = "forestplot_v2.pdf", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 11, height = 6, units = "in")


```




\newpage
# Endline Treatment Effect -- Controlling for Baseline Measurements


```{r Prepping and joining baseline data}


#cen dataset

#Defining bl variables to select
cen_vars <- c("unique_id","village","prim_source_jjm", "sec_source",
                  "jjm_drinking", "water_treat_binary" 
                  # Not in data "tap_issues_taste", "time_spent_treat", "time_spent_treat_15", "time_spent_treat_5"
                  )

#Selecting census variables to keep
cen_model <- cen%>%
  dplyr::select(all_of(cen_vars))%>%
  rename(bl_prim_source_jjm = "prim_source_jjm")%>%
  rename(bl_sec_source = "sec_source")%>%
  rename(bl_jjm_drinking = "jjm_drinking")%>%
  rename(bl_water_treat_binary = "water_treat_binary")

#Summarizing stats for each village
cen_model <- cen_model%>%
  group_by(village)%>%
  summarise(
    bl_prim_source_jjm = mean(bl_prim_source_jjm, na.rm = TRUE),
    bl_sec_source = mean(bl_sec_source, na.rm = TRUE),
    bl_jjm_drinking = mean(bl_jjm_drinking, na.rm = TRUE),
    bl_water_treat_binary = mean(bl_water_treat_binary, na.rm = TRUE)
  )


#Gathering baseline variable names
cen_model_vars <- colnames(cen_model)[-1]


#bl dataset

bl_vars <- c("unique_id","village","treat_time_5min") #But can I use this to control for baseline data if the dataset is partial?
#Selecting census variables to keep
bl_model <- bl%>%
  dplyr::select(all_of(bl_vars))%>%
  rename(bl_treat_time_5min = "treat_time_5min")

#Summarizing stats for each village
bl_model <- bl_model%>%
  group_by(village)%>%
  summarise(
    bl_treat_time_5min = mean(bl_treat_time_5min, na.rm = TRUE)
  )


#Gathering baseline variable names
bl_model_vars <- colnames(bl_model)[-1]




#IDEXX - Standard

#make unique id a character from "idexx" so it can be joined
#filter for sample type

idexx_bl_tap <- idexx%>%
  filter(sample_type == "Tap")%>%
  dplyr::select(unique_id, village, cf_log, ec_log#, cf_log, ec_log
                )%>%
  rename(bl_cf_pa_tap = "cf_log")%>%
  rename(bl_ec_pa_tap = "ec_log")%>%
  # rename(cf_log_tap = "cf_log")%>%
  # rename(ec_log_tap = "ec_log")%>%
  mutate(unique_id = as.character(unique_id))

#Summarizing stats for each village
idexx_bl_tap <- idexx_bl_tap%>%
  group_by(village)%>%
  summarise(
    bl_cf_pa_tap = mean(bl_cf_pa_tap, na.rm = TRUE),
    bl_ec_pa_tap = mean(bl_ec_pa_tap, na.rm = TRUE)
  )

idx_tap_vars <- colnames(idexx_bl_tap)[-1]

idexx_bl_stored <- idexx%>%
  filter(sample_type == "Stored")%>%
  dplyr::select(unique_id, village, cf_log, ec_log#, cf_log, ec_log
                )%>%
  rename(bl_cf_pa_stored = "cf_log")%>%
  rename(bl_ec_pa_stored = "ec_log")%>%
  # rename(cf_log_stored = "cf_log")%>%
  # rename(ec_log_stored = "ec_log")%>%
  mutate(unique_id = as.character(unique_id))

#Summarizing stats for each village
idexx_bl_stored <- idexx_bl_stored%>%
  group_by(village)%>%
  summarise(
    bl_cf_pa_stored = mean(bl_cf_pa_stored, na.rm = TRUE),
    bl_ec_pa_stored = mean(bl_ec_pa_stored, na.rm = TRUE)
  )


idx_stored_vars <- colnames(idexx_bl_stored)[-1]



#IDEXX - ABR 
idexx_bl_abr_tap <- idexx_abr%>%
  filter(data_round == "BL")%>%
  filter(sample_type == "Tap")%>%
  dplyr::select(unique_id, village, ec_log
                )%>%
  rename(bl_ec_abr_tap = "ec_log")%>%
  mutate(unique_id = as.character(unique_id))

#Summarizing stats for each village
idexx_bl_abr_tap <- idexx_bl_abr_tap%>%
  group_by(village)%>%
  summarise(
    bl_ec_abr_tap = mean(bl_ec_abr_tap, na.rm = TRUE)
  )

abr_tap_vars <- colnames(idexx_bl_abr_tap)[-1]


idexx_bl_abr_stored <- idexx_abr%>%
  filter(data_round == "BL")%>%
  filter(sample_type == "Stored")%>%
  dplyr::select(unique_id, village, ec_log
                )%>%
  rename(bl_ec_abr_stored = "ec_log")%>%
  mutate(unique_id = as.character(unique_id))

#Summarizing stats for each village
idexx_bl_abr_stored <- idexx_bl_abr_stored%>%
  group_by(village)%>%
  summarise(
    bl_ec_abr_stored = mean(bl_ec_abr_stored, na.rm = TRUE)
  )

abr_stored_vars <- colnames(idexx_bl_abr_stored)[-1]





#Joining data to endline dataset
el_model <- el%>%
  left_join(cen_model, by = "village")%>%
  left_join(bl_model, by = "village")
  
  
  
#Joining IDEXX data
#Removing BL data
idexx_fu <- idexx_tab%>%
  filter(data_round != "BL")

#Separating by tap and stored water
idexx_fu_tap <- idexx_fu%>%
  filter(sample_type == "Tap")%>%
  mutate(unique_id = as.character(unique_id))

idexx_fu_stored <- idexx_fu%>%
  filter(sample_type == "Stored")%>%
  mutate(unique_id = as.character(unique_id))

#Joining datasets
idexx_fu_tap <- idexx_fu_tap%>%
  left_join(idexx_bl_tap, by = "village")

idexx_fu_stored <- idexx_fu_stored%>%
  left_join(idexx_bl_stored, by = "village")



#Removing BL data
idexx_abr_fu <- idexx_abr%>%
  filter(data_round != "BL")

#Separating by tap and stored water
idexx_abr_tap <- idexx_abr_fu%>%
  filter(sample_type == "Tap")%>%
  mutate(unique_id = as.character(unique_id))

idexx_abr_stored <- idexx_abr_fu%>%
  filter(sample_type == "Stored")%>%
  mutate(unique_id = as.character(unique_id))

#Joining datasets
idexx_abr_tap <- idexx_abr_tap%>%
  left_join(idexx_bl_abr_tap, by = "village")

idexx_abr_stored <- idexx_abr_stored%>%
  left_join(idexx_bl_abr_stored, by = "village")
  







```


```{r Endline Treatment Effect -- Controlling for Baseline Measurements}

#Survey Outcomes --- 

outcome_vars <- c("prim_source_jjm", "sec_source", #Issue after code cleaning updates
                  "jjm_drinking", "water_treat_binary", "time_spent_treat_5")

bl_vars <- c("bl_prim_source_jjm", "bl_sec_source", "bl_jjm_drinking", "bl_water_treat_binary",
              "bl_treat_time_5min")



el_model <- factormaker(el_model, outcome_vars) #Making variables numeric
el_model <- factormaker(el_model, bl_vars) #Making variables numeric



#Poisson Regression
all_models <- mapply(
                     function(var, bl_var) {
                       ilc_glm_bl(data = el_model, var = var, bl_var = bl_var)
                       },  
                     outcome_vars, bl_vars,
                     SIMPLIFY = FALSE)

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
el_models <- ilc_model_table_only(all_models)
ilc_model_table(all_models)



























# Poisson Regression - Treatment Effect -------------------------------------------------


#Running Poisson Regression on Tap Samples ----


outcome_vars <- c("cf_pa_binary","ec_pa_binary") #Selecting outcome variables
bl_vars <- c("bl_cf_pa_tap", "bl_ec_pa_tap")


idexx_model <- factormaker(idexx_fu_tap, outcome_vars) #Converting to numeric type
idexx_model <- factormaker(idexx_fu_tap, bl_vars)

#Running all models
#Poisson regression
all_models <- mapply(
                     function(var, bl_var) {
                       ilc_glm_bl(data = idexx_model, var = var, bl_var = bl_var)
                       },  
                     outcome_vars, bl_vars,
                     SIMPLIFY = FALSE)

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_tap <- ilc_model_table_only(all_models)
idexx_poisson_tap <- idexx_poisson_tap%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_tap", "ec_tap"))%>%
  mutate(sample_type = "Tap")


#Running Poisson Regression on Stored Samples ----

outcome_vars <- c("cf_pa_binary","ec_pa_binary") #Selecting outcome variables
bl_vars <- c("bl_cf_pa_stored", "bl_ec_pa_stored")


idexx_model <- factormaker(idexx_fu_stored, outcome_vars) #Converting to numeric type
idexx_model <- factormaker(idexx_fu_stored, bl_vars)

#Running all models
#Poisson regression
all_models <- mapply(
                     function(var, bl_var) {
                       ilc_glm_bl(data = idexx_model, var = var, bl_var = bl_var)
                       },  
                     outcome_vars, bl_vars,
                     SIMPLIFY = FALSE)

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_stored <- ilc_model_table_only(all_models)
idexx_poisson_stored <- idexx_poisson_stored%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_stored", "ec_stored"))%>%
  mutate(sample_type = "Stored")


idexx_poisson <- rbind(idexx_poisson_tap, idexx_poisson_stored)






















#Antibiotic Resistance Results ----


  

#Running Poisson Regression on Tap Samples ----

outcome_vars <- c("ec_pa_binary") #Selecting outcome variables
bl_vars <- c("bl_ec_abr_tap")


idexx_model <- factormaker(idexx_abr_tap, outcome_vars) #Converting to numeric type
idexx_model <- factormaker(idexx_model, bl_vars)

#Running all models
#Poisson regression
all_models <- mapply(
                     function(var, bl_var) {
                       ilc_glm_bl(data = idexx_model, var = var, bl_var = bl_var)
                       },  
                     outcome_vars, bl_vars,
                     SIMPLIFY = FALSE)


#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_tap <- ilc_model_table_only(all_models)
idexx_poisson_tap <- idexx_poisson_tap%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_tap", "ec_tap"))%>%
  mutate(sample_type = "Tap")


#Running Poisson Regression on Stored Samples ----

outcome_vars <- c("ec_pa_binary") #Selecting outcome variables
bl_vars <- c("bl_ec_abr_stored")


idexx_model <- factormaker(idexx_abr_stored, outcome_vars) #Converting to numeric type
idexx_model <- factormaker(idexx_model, bl_vars)

#Running all models
#Poisson regression
all_models <- mapply(
                     function(var, bl_var) {
                       ilc_glm_bl(data = idexx_model, var = var, bl_var = bl_var)
                       },  
                     outcome_vars, bl_vars,
                     SIMPLIFY = FALSE)

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
idexx_poisson_stored <- ilc_model_table_only(all_models)
idexx_poisson_stored <- idexx_poisson_stored%>%
  mutate(model_name = ifelse(model_name == "cf_pa_binary", "cf_stored", "ec_stored"))%>%
  mutate(sample_type = "Stored")


idexx_abr_poisson <- rbind(idexx_poisson_tap, idexx_poisson_stored)




















#Updating idexx_poisson
idexx_poisson <- idexx_poisson%>%
  dplyr::select(!(sample_type))


#Updating idexx_abr_poisson
idexx_abr_poisson <- idexx_abr_poisson%>%
  filter(model_name != "cf_tap")%>%
  filter(model_name != "cf_stored")%>%
  mutate(model_name = ifelse(model_name == "ec_stored","Presence Antibiotic Resistant E. coli in Stored Water", "Presence Antibiotic Resistant E. coli in Tap Water"))%>%
  select(!(sample_type))


#Joining poisson results
el_models_forestplot <- rbind(idexx_poisson, idexx_abr_poisson, el_models)

#Setting order of variables
#Changing model names
el_models_forestplot <- el_models_forestplot%>%
  mutate(mean = estimate)%>%
  mutate(estimate = as.character(round(estimate, 2)))%>%
  mutate(Lower_CI = round(Lower_CI, 2))%>%
  mutate(Upper_CI = round(Upper_CI, 2))%>%
  mutate(estimate = paste0(estimate, " (", Lower_CI, ", ", Upper_CI, ")"))%>%
  mutate(lower = Lower_CI)%>%
  mutate(upper = Upper_CI)%>%
  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))




el_models_forestplot$model_name <- el_models_forestplot$model_name%>%
  factor()%>%
  fct_recode("Presence of Total Coliform at Taps"= "cf_tap",
              "Presence of E. coli at Taps"= "ec_tap",
              "Presence of Total Coliform in Stored Water"= "cf_stored",
              "Presence of E. coli in Stored Water"= "ec_stored",
             "Presence Antibiotic Resistant E. coli in Stored Water" =
              "Presence Antibiotic Resistant E. coli in Stored Water",
             "Taps as Primary Source" = "prim_source_jjm",
             "Use a Secondary Source" = "sec_source",
             "Drink Tap Water" = "jjm_drinking",
             "Treat Water" = "water_treat_binary",
             "Time Spent Treating Water is >5 Minutes" = "time_spent_treat_5"
             )
#Reordering
el_models_forestplot$model_name <- factor(el_models_forestplot$model_name, levels = 
                                            c(
             "Time Spent Treating Water is >5 Minutes",
             "Treat Water",
             "Drink Tap Water",
              "Use a Secondary Source",
             "Taps as Primary Source",
             "Presence Antibiotic Resistant E. coli in Stored Water",
              "Presence Antibiotic Resistant E. coli in Tap Water",
             "Presence of E. coli in Stored Water",
             "Presence of Total Coliform in Stored Water",
             "Presence of E. coli at Taps",
             "Presence of Total Coliform at Taps"
             ))

el_models_forestplot <- el_models_forestplot%>%
  mutate(variable_type = ifelse(model_name %in% c("Presence Antibiotic Resistant E. coli in Stored Water",
              "Presence Antibiotic Resistant E. coli in Tap Water",
             "Presence of E. coli in Stored Water",
             "Presence of Total Coliform in Stored Water",
             "Presence of E. coli at Taps",
             "Presence of Total Coliform at Taps"), "Water Quality Outcome", "Behavioral Outcome"))


#Manually adding in column names to the figure
# el_models_forestplot <- el_models_forestplot%>%
#   bind_rows(
#     data.frame(
#       model_name = "Outcome",
#       covariate = NA,
#       estimate = "Prevalence Ratio (95% CI)",
#       std_error = NA,
#       p_value = "P-value",
#       N = NA,
#       Lower_CI = NA,
#       Upper_CI = NA,
#       signif = NA,
#       mean = NA,
#       lower = NA,
#       upper = NA
#     ))
#This is not a good option


#Creating Foresplot using ggplot

## Create plot 
p_forestplot <- ggplot(el_models_forestplot, aes(x = mean, y = model_name)) +
  geom_point(aes(color = variable_type), size = 2) +  
  geom_errorbarh(aes(xmin = Lower_CI, xmax = Upper_CI,  color = variable_type), height = 0.2) + 
  geom_vline(xintercept = 1, linetype = "dashed", color = "black") +# Dashed line at x = 1 (null Risk Ratio)
  scale_y_discrete(labels = function(y) str_wrap(y, width = 35)) +
  scale_x_continuous(limits = c(0.15, 1.90), breaks = c(0.25, 0.50, 0.75, 1.00, 1.2))+
  scale_color_manual(values = c("Water Quality Outcome" = "#00008B", "Behavioral Outcome" = "#EEA944"))+
  labs(
    x = "Prevalence Ratio", 
    y = "Outcome") + 
  theme_classic() +
  theme(legend.title = element_blank(),
        axis.text.y = element_text(size = 10), 
        axis.title.y = element_text(size = 13),
        axis.title.x = element_text(size = 13)) #+
  #guides(color = guide_legend(reverse = TRUE)) # Ensures the order of the legend matches the order in which point estimates appear on the plot

# Add horizontal lines between levels of outcomes to create separation
y_levels <- levels(factor(el_models_forestplot$model_name))
y_positions <- seq_along(y_levels) - 0.5
for (y in y_positions) {
  p_forestplot <- p_forestplot + geom_hline(yintercept = y, color = "darkgrey", linetype = "solid", linewidth = 0.5)
}

#Adding in effect estimates and p-values
p_forestplot <- p_forestplot + 
  geom_text(aes(label = estimate, x = max(Upper_CI) + 0.25), hjust = 0, size = 3) + 
    geom_text(aes(label = p_value, x = max(Upper_CI) + 0.50), hjust = 0, size = 3) + 
    geom_text(aes(label = N, x = max(Upper_CI) + 0.65), hjust = 0, size = 3)
  

#Viewing
p_forestplot

ggsave(filename = "forestplot_bl_control_v1.pdf", path = (paste0(github_path(), "/3_manuscript/figures")), dpi = 1080, width = 11, height = 6, units = "in")





```


