---
title: "India ILC - Pilot Manuscript 2024"
author: "Jeremy Lowe"
date: "`r Sys.Date()`"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, message = FALSE)

```

# Introduction


```{r package loading, include=FALSE}

library(rsurveycto)
library(expss)
library(labelled)
library(httr)
library(lubridate)
library(quantitray)
library(sjmisc)
library(knitr)
library(kableExtra)
library(readxl)
library(experiment)
library(stargazer)
library(readxl)
library(haven)
library(googlesheets4)
library(ggsignif)
library(patchwork)
library(table1)
library(gtsummary)
library(gt)
library(webshot2)
library(clubSandwich)
library(sandwich)
library(lmtest)
library(broom)
library(tidyverse)
library(sf)
library(gridExtra)



```



```{r profile}
#------------------------ setting user path ----------------------------------------#

# setting github directory
github_path <- function() {
  user <- Sys.info()["user"]
  if (user == "asthavohra") {
    github = "/Users/asthavohra/Documents/GitHub/i-h2o-india/Code/2_Pilot/0_pilot logistics/"
  } 
  else if (user=="akitokamei"){
    github = "/Users/akitokamei/Library/CloudStorage/Dropbox/Mac/Documents/GitHub/i-h2o-india/Code/2_Pilot/0_pilot logistics/"
  } 
  else if (user == "jerem") {
    github = "C:/Users/jerem/Documents/i-h2o-india/Code"
  } 
  else {
    warning("No path found for current user (", user, ")")
    github = getwd()
  }
  
  stopifnot(file.exists(github))
  return(github)
}

github <- github_path()



#Setting all other user paths

source(paste0(github_path(),"/3_manuscript/0-config.R"))



```


# Loading Data

```{r dataset loading}

#Loading different final datasets from Box
#See Process Doc for details on cleaning code and clean datasets:
#https://docs.google.com/document/d/1Hpv5HF5ICO5FSVdQnPtDECCYORn2qy5S7C_KIx0pDuM/edit


#from Box

#bl_raw <- read_csv(paste0(user_path(), "/1_raw/Baseline follow up survey_WIDE.csv"))

#Baseline Survey
bl <- read_stata(paste0(user_path(), "/3_final/1_2_Followup_cleaned.dta"))

#Baseline Census
cen <- read_stata(paste0(user_path(),"/3_final/Final_HH_Odisha_consented_Full.dta"))

#Round 1 survey
r1 <- read_stata(paste0(user_path(),"/3_final/1_5_followup_R1_cleaned.dta"))

#Round 2 survey
r2 <- read_stata(paste0(user_path(),"/3_final/1_6_followup_R2_cleaned.dta"))

#Round 3 survey
r3 <- read_stata(paste0(user_path(),"/3_final/1_7_followup_R3_cleaned.dta"))

#Chlorine Monitoring Survey
mon <- read_stata(paste0(user_path(),"/3_final/1_X_chlorine_monitoring.dta"))

#Longitudinal chlorine monitoring form
#mon_full <- read_csv("C:/Users/jerem/Box/India Water project/2_Pilot/Data/1_raw/india_ilc_pilot_monitoring_WIDE.csv")

gv <- read_csv(paste0(user_path(), "/6_Gram Vikas/India ILC - Gram Vikas Chlorine Monitoring_current.csv"))

#Baseline IDEXX
idexx <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/BL_idexx_master_cleaned.csv"))

#Baseline ABR IDEXX
#abr <- read_xlsx("C:/Users/jerem/Box/India Water project/2_Pilot/Data/5_lab data/idexx/raw/_India ILC_ABR_data_MASTER.xlsx", skip = 1)

#IDEXX Round 1
idexx_r1 <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/R1_idexx_master_cleaned.csv"))


#IDEXX Round 2
idexx_r2 <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/R2_idexx_master_cleaned.csv"))

#IDEXX Round 3
idexx_r3 <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/R3_idexx_master_cleaned.csv"))

#Pooled IDEXX Rounds
idexx_tab <- read_csv(paste0(user_path(),"/5_lab data/idexx/cleaned/POOLED_idexx_master_cleaned.csv"))

#Checking Michelle's cleaned IDEXX data
idexx_mc <- read_stata(paste0(user_path(),"/2_deidentified/Ecoli results followup_cleaned_WIDE.dta"))

#Village Details
#village_details_old <- read_xlsx(paste0(user_path(),"/5_lab data/India_ILC_Pilot_Rayagada_Village_Tracking.xlsx")) #Old method

village_details <- read_sheet("https://docs.google.com/spreadsheets/d/1iWDd8k6L5Ny6KklxEnwvGZDkrAHBd0t67d-29BfbMGo/edit?pli=1#gid=1710429467")

#Village Details
villages <- read_stata(paste0(user_path(),"4_other/India ILC_Pilot_Rayagada Village Tracking_clean_final.dta" ))


#Cen final
cen_info <- read_stata(paste0(user_path(),"3_final/Final_Population_Village.dta" ))


#endline census
el <- read_stata(paste0(user_path(),"3_final/1_8_Endline_Census_cleaned.dta" ))

#map data - shapefile
shp_file_0 <- st_read(paste0(user_path(), "7_map/shapefiles/gadm41_IND_0.shp"))
shp_file_1 <- st_read(paste0(user_path(), "7_map/shapefiles/gadm41_IND_1.shp"))
shp_file_2 <- st_read(paste0(user_path(), "7_map/shapefiles/gadm41_IND_2.shp"))
shp_file_3 <- st_read(paste0(user_path(), "7_map/shapefiles/gadm41_IND_3.shp"))




```


# Defining Functions

```{r defining misc functions}

source(paste0(github_path(),"/3_manuscript/1-functions.R"))

```



\newpage
# Data Cleaning


```{r Data cleaning R code}

#Calling script to clean loaded data
source(paste0(github_path(),"/3_manuscript/India ILC Pilot - Manuscript Data Cleaning 2024.R"))


```


\newpage
# Analysis


## Odisha Map

```{r Odisha map}

#Map of India
map_p1 <- ggplot() +
  geom_sf(data = shp_file_0, fill = "white", color = "black") +  # Base map for India
  geom_sf(data = shp_file_1, fill = "white", color = "black") +  # Base map for Odisha
  geom_sf(data = rayagada, fill = "red", color = "black") +  # Highlight Rayagada
  theme_minimal() +
  ggtitle("") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )


#map_p1


#Map of Odisha

map_p2 <- ggplot() +
  #geom_sf(data = shp_file_0, fill = "white", color = "black") +  # Base map for India
  geom_sf(data = odisha, fill = "white", color = "black") +  # Base map for Odisha
  geom_sf(data = rayagada, fill = "red", color = "black") +  # Highlight Rayagada
  theme_minimal() +
  ggtitle("") +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )

#map_p2


#Combining maps
combined_plot <- grid.arrange(map_p1, map_p2, ncol = 2)

combined_plot

```





## Desc Stats - Household Characteristics

```{r}




```




## Chlorine Monitoring -- Household Surveys

```{r Chlorine Monitoring -- Surveys}


#Using pooled survey data to track % of positive chlorine samples alongside average chlorine dose

#Selecting for follow-up rounds
summary_rounds <- all_rounds%>%
  filter(data_round != "BL")%>%
  filter(assignment == "Treatment")%>%
  filter(village != "Karnapadu")


#Making desc stat table for summarizing chlorine results from followup
desc_stats <- summary_rounds%>%
  group_by(village_code, data_round)%>%
  summarise(
    "Number of Samples" = n(),
    "Tap - % Positive for Free Chlorine (> 0.1 mg/L)" = round((sum(fc_tap_binary == 1) / n()) * 100, 1),
    "Tap - Average Concentration (mg/L)" = mean(fc_tap_avg, na.rm = TRUE)#,
    #"Stored - % Positive for Free Chlorine (> 0.1 mg/L)" = round((sum(fc_stored_binary == 1) / n()) * 100, 1),
    #"Stored - Average Concentration (mg/L)" = mean(fc_stored_avg, na.rm = TRUE)
    )


#Creating plot
#Percentage of samples that test positive
cl_summary <- ggplot(data = desc_stats) + 
  geom_col(aes(x = data_round, y = `Tap - % Positive for Free Chlorine (> 0.1 mg/L)`), position = "dodge") +
  geom_text(aes(x = data_round, y = `Tap - % Positive for Free Chlorine (> 0.1 mg/L)`,
                label = paste0(round(`Tap - % Positive for Free Chlorine (> 0.1 mg/L)`, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  #Adding text for average chlorine concentration to the plot
  geom_text(aes(x = data_round, y = `Tap - % Positive for Free Chlorine (> 0.1 mg/L)`,
                label = paste0(round(`Tap - Average Concentration (mg/L)`, 2), " mg/L")),
            position = position_dodge(width = 0.9), vjust = 1, color = "white", size = 3) +
    facet_wrap(~village_code, ncol = 3)+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Data Collection Round", 
       y = "% Taps Positive for Free Chlorine (> 0.1 mg/L)",
       title = "Presence of Chlorine in Tap Connections During Household Survey Rounds",
       caption = "Average chlorine concentrations are displayed in white text in each figure"
       )+
  theme_bw() #+ 
  #theme(axis.text.x = element_text(angle=0, vjust=1, hjust=1))

cl_summary



# desc_stats <- all_rounds%>%
#   dplyr::select("data_round", "village", "fc_tap_binary",
#                 "fc_stored_binary", "fc_tap_avg", "fc_stored_avg")%>%
#   tbl_strata(
#     strata = data_round,
#     .tbl_fun =
#       ~ .x %>%
#         tbl_summary(by = village, 
#                     missing = "no",
#                     type = c("fc_tap_binary",
#                              "fc_stored_binary",
#                              "fc_tap_avg",
#                              "fc_stored_avg") ~ "continuous",
#                     statistic = list(
#                       all_continuous() ~ "{mean} ({sd})",
#                       all_categorical() ~ "{p}%"),
#                     digits = list(all_continuous() ~ 2, 
#                                   all_categorical() ~ 0),
#                     label = list(
#                                  fc_tap_binary ~ "Presence of free chlorine in taps (>0.1 mg/L)",
#                                  fc_stored_binary ~ "Presence of free chlorine in stored water (>0.1 mg/L)",
#                                  fc_tap_avg ~ "Average tap free chlorine concentration (mg/L)" ,
#                                  fc_stored_avg ~ "Average stored water free chlorine concentration (mg/L)"
#                                  )
#                     )%>%
#      modify_footnote(all_stat_cols() ~ "Mean (SD)"),
#     .header = "**{strata}**"
#   )%>%
#   modify_footnote(update =  ~ "Mean (SD); BL - Oct 2023, R1 - February 2024, R2 - March 2024, R3 - April 2024")
# 
# desc_stats <- as_gt(desc_stats)%>%
#   tab_options(table.font.size = 11)



```


## Chlorine Monitoring -- Weekly

```{r Chlorine Monitoring -- Weekly}


#All village plot
  cl_p1 <- ggplot(data = mon) + 
    geom_point(aes(x = test_date, y = chlorine_concentration,
                   color = chlorine_test))+
    geom_line(aes(x = test_date, y = chlorine_concentration,
                  color = chlorine_test))+
    geom_hline(yintercept=0.20, linetype="dashed", color = "red")+
    geom_hline(yintercept=0.60, linetype="dashed", color = "red")+
    scale_y_continuous(
                     limits = c(0, 1.5),
                     expand = c(0,0))+
    labs(x = "Date", 
       y = "Chlorine Concentration (mg/L)",
       color = "Sample Type",
       title = (paste("JPAL ILC Chlorine Monitoring for 2024")))+
    theme_bw() + 
    theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))+
    facet_wrap(~village_name, ncol = 3)+
    geom_vline(data = gv_refill, aes(xintercept = refill_date_0),
               linetype = "dashed", color = "darkgreen")+
      #annotate("text", x = as.Date("2024-04-08"), y = 0.1, label = "Refill",
       #        angle = 0, vjust = -0.5, size = 3, color = "darkgreen")
    #annotate("label", x = as.Date("2024-04-10"), y = 1.5, label = "         ", angle = 0, 
     #      vjust = -0.5, color = "black", size = 12, fill = "white", label.size = NA)+
    geom_text(data = filter(mon, village_name == "Asada"), 
            aes(x = as.Date("2024-04-12"), y = 1.08), 
            label = "Refill", angle = 0, vjust = -0.5, color = "darkgreen", size = 3)+
    geom_text(data = filter(mon, village_name == "Asada"), 
            aes(x = as.Date("2024-04-18"), y = 1.2), 
            label = "Target Range", angle = 0, vjust = -0.5, color = "red", size = 3)
  
cl_p1



#Summary of monitoring data across all villages
  
cl_p2 <- ggplot(data = mon_summary_weekly) + 
    geom_point(aes(x = test_week, y = avg_concentration,
                   color = chlorine_test))+
    geom_line(aes(x = test_week, y = avg_concentration,
                  color = chlorine_test))+
    geom_hline(yintercept=0.20, linetype="dashed", color = "red")+
    geom_hline(yintercept=0.60, linetype="dashed", color = "red")+
    scale_y_continuous(
                     limits = c(0, 2.0),
                     expand = c(0,0))+
    labs(x = "Date", 
       y = "Chlorine Concentration (mg/L)",
       color = "Sample Type",
       title = (paste0("Chlorine Monitoring - February-June 2024")),
       caption = "Concentrations were averaged on a weekly-basis across the 10 treatment villages.")+
    theme_bw() + 
    theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))
  
  
cl_p2


#Percentage of samples that test positive
cl_p3 <- ggplot(data = mon_summary_percent_1) + 
  geom_col(aes(x = chlorine_test, y = `% Positive for Free Chlorine`), position = "dodge") +
  geom_text(aes(x = chlorine_test, y = `% Positive for Free Chlorine`,
                label = paste0(round(`% Positive for Free Chlorine`, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
    facet_wrap(~village, ncol = 3)+
    #geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      #fill = assignment), position = position_dodge(width = 0.9),
                 #width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Location", 
       y = "% Positive for Free Chlorine (> 0.1 mg/L)",
       title = "Positive chlorine samples during weekly monitoring - April-June 2024"
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

cl_p3


#Percentage of samples that test positive
cl_p4 <- ggplot(data = mon_summary_percent_2) + 
  geom_col(aes(x = chlorine_test, y = `% Positive for Free Chlorine`), position = "dodge") +
  geom_text(aes(x = chlorine_test, y = `% Positive for Free Chlorine`,
                label = paste0(round(`% Positive for Free Chlorine`, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
    #facet_wrap(~village, ncol = 3)+
    #geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      #fill = assignment), position = position_dodge(width = 0.9),
                 #width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Location", 
       y = "% Positive for Free Chlorine (> 0.1 mg/L)",
       title = "Positive chlorine samples during weekly monitoring - April-June 2024"
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

cl_p4




#Comparing % of positive samples in each village compared to their average chlorine dose






```



## Desc Stats - Microbiological Contamination



### Baseline

```{r Microbiological Contamination - Baseline}


# Calculate descriptive statistics by village
village_stats_bl <- village_stats(idexx)

tc_stats_bl <- tc_stats(idexx)

all_stats_bl <- all_stats(idexx)




#Creating risk level stats for WHO Risk plot
risk_stats_bl <- risk_stats(idexx)


# Print the table
kbl(village_stats_bl)%>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
  add_header_above(c("Baseline - Water Quality Test Results " = 7)) %>%
  row_spec(0, bold = TRUE, color = "black", background = "white") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, width = "75px")

kbl(tc_stats_bl)%>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
  add_header_above(c("Baseline - Water Quality Test Results " = 11)) %>%
  row_spec(0, bold = TRUE, color = "black", background = "white") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, width = "75px")

kbl(all_stats_bl)%>%
  kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
  add_header_above(c("Baseline - Water Quality Test Results " = 6)) %>%
  row_spec(0, bold = TRUE, color = "black", background = "white") %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, width = "75px")



#Plotting IDEXX E. coli data per village
p1 <- ggplot(data = idexx) + 
  geom_boxplot(aes(x = village, y = ec_log, fill = sample_type)) +
  scale_y_continuous(
                     limits = c(0, 4),
                     expand = c(0,0))+
  labs(x = "Village", 
       y = expression(paste("log10(MPN ",italic("E. coli"), "/100 mL)")),
       title = expression(paste(italic("E. coli"), " Baseline Presence in Tap and Stored Drinking Water in Odisha (N = 160)")))+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

#p1



#Plotting IDEXX E. coli data by sample type
p4 <- ggplot(data = idexx) + 
  geom_boxplot(aes(x = sample_type, y = ec_log)) +
  scale_y_continuous(
                     limits = c(0, 4),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("log10(MPN ",italic("E. coli"), "/100 mL)")),
       title = expression(paste(italic("E. coli"), " Baseline Presence in Tap and Stored Drinking Water in Odisha (N = 160)")))+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

#p4




#Plotting treatment/control stats on a bar plot
p_ec_bl <- ggplot(data = tc_stats_bl) + 
  geom_col(aes(x = sample_type, y = `% Positive for E. coli`, fill = assignment), position = "dodge") +
  geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                    fill = assignment), position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "BL - Oct 2023"
       #title = expression(paste(italic("E. coli"), " BL - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_bl <- ggplot(data = tc_stats_bl) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "BL - Oct 2023"
       #title = expression(paste(" BL - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_bl + p_ec_bl




#Making WHO risk plot
p_ec_risk_bl <- ggplot(data = risk_stats_bl) + 
  geom_bar(aes(x = assignment, y = `E. coli Risk Levels %`, fill = ec_risk), position = "stack", stat = "identity") +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Assignment", 
       y = expression(paste("% for each risk category")),
       fill = expression(paste(italic("E. coli"), " Risk Categories")),
       title = "BL - Oct 2023"
       #title = expression(paste(" BL - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))



```

### Follow-up Surveys

#### Need to figure out robust standard errors issues

```{r Microbiological Contamination -- Follow-up R1}


#Removing NA result
idexx_r1 <- idexx_r1%>%
  filter(is.na(ec_mpn) == FALSE)

# Calculate descriptive statistics by village
village_stats_r1 <- village_stats(idexx_r1)

tc_stats_r1 <- tc_stats(idexx_r1)


all_stats_r1 <- all_stats(idexx_r1)


#Creating risk level stats for WHO Risk plot
risk_stats_r1 <- risk_stats(idexx_r1)

# Print the table
# kbl(village_stats_r1)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("R1 - Water Quality Test Results " = 7)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")

# kbl(tc_stats_r1)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("R1 - Water Quality Test Results " = 11)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")
# 
# 
# kbl(all_stats_r1)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("R1 - Water Quality Test Results " = 6)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")



#Plotting treatment/control stats on a bar plot
p_ec_r1 <- ggplot(data = tc_stats_r1) + 
  geom_col(aes(x = sample_type, y = `% Positive for E. coli`, fill = assignment), position = "dodge") +
  geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                    fill = assignment), position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "R1 - February 2024"
       #title = expression(paste(italic("E. coli"), " R1 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_r1 <- ggplot(data = tc_stats_r1) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "R1 - February 2024"
       #title = expression(paste(" R1 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_r1 + p_ec_r1

#Fisher's Exact Test for differences between control and treatment
idexx_r1_stored <- idexx_r1%>%
  filter(sample_type == "Stored")

idexx_r1_tap <- idexx_r1%>%
  filter(sample_type == "Tap")

stored_cf <- fisher.test(x = idexx_r1_stored$assignment, y=idexx_r1_stored$cf_pa)

stored_ec <- fisher.test(x = idexx_r1_stored$assignment, y=idexx_r1_stored$ec_pa)

tap_cf <- fisher.test(x = idexx_r1_tap$assignment, y=idexx_r1_tap$cf_pa)

tap_ec <- fisher.test(x = idexx_r1_tap$assignment, y=idexx_r1_tap$ec_pa)

idexx_r1_signif <- data.frame(stored_cf$p.value, stored_ec$p.value, tap_cf$p.value, tap_ec$p.value)



#Making WHO risk plot
p_ec_risk_r1 <- ggplot(data = risk_stats_r1) + 
  geom_bar(aes(x = assignment, y = `E. coli Risk Levels %`, fill = ec_risk), position = "stack", stat = "identity") +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Assignment", 
       y = expression(paste("% for each risk category")),
       fill = expression(paste(italic("E. coli"), " Risk Categories")),
       title = "R1 - February 2024"
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))





```


```{r Microbiological Contamination -- Follow-up R2}


#Removing NA result
idexx_r2 <- idexx_r2%>%
  filter(is.na(ec_mpn) == FALSE)%>%
  filter(sample_type != "Blank")%>% #Removing blanks
  filter(sample_type != "Solar") #Removing solar water samples

# Calculate descriptive statistics by village
village_stats_r2 <- village_stats(idexx_r2)

tc_stats_r2 <- tc_stats(idexx_r2)


all_stats_r2 <- all_stats(idexx_r2)


#Creating risk level stats for WHO Risk plot
risk_stats_r2 <- risk_stats(idexx_r2)

# Print the table
# kbl(village_stats_r2)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("r2 - Water Quality Test Results " = 7)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")
# 
# kbl(tc_stats_r2)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("r2 - Water Quality Test Results " = 11)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")
# 
# 
# kbl(all_stats_r2)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("r2 - Water Quality Test Results " = 6)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")
# 
# 


#Plotting treatment/control stats on a bar plot
p_ec_r2 <- ggplot(data = tc_stats_r2) + 
  geom_col(aes(x = sample_type, y = `% Positive for E. coli`, fill = assignment), position = "dodge") +
  geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                    fill = assignment), position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "R2 - March 2024"
       #title = expression(paste(italic("E. coli"), " r2 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_r2 <- ggplot(data = tc_stats_r2) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "R2 - March 2024"
       #title = expression(paste(" r2 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_r2 + p_ec_r2

#Fisher's Exact Test for differences between control and treatment
idexx_r2_stored <- idexx_r2%>%
  filter(sample_type == "Stored")

idexx_r2_tap <- idexx_r2%>%
  filter(sample_type == "Tap")

stored_cf <- fisher.test(x = idexx_r2_stored$assignment, y=idexx_r2_stored$cf_pa)

stored_ec <- fisher.test(x = idexx_r2_stored$assignment, y=idexx_r2_stored$ec_pa)

tap_cf <- fisher.test(x = idexx_r2_tap$assignment, y=idexx_r2_tap$cf_pa)

tap_ec <- fisher.test(x = idexx_r2_tap$assignment, y=idexx_r2_tap$ec_pa)

idexx_r2_signif <- data.frame(stored_cf$p.value, stored_ec$p.value, tap_cf$p.value, tap_ec$p.value)



#Making WHO risk plot
p_ec_risk_r2 <- ggplot(data = risk_stats_r2) + 
  geom_bar(aes(x = assignment, y = `E. coli Risk Levels %`, fill = ec_risk), position = "stack", stat = "identity") +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Assignment", 
       y = expression(paste("% for each risk category")),
       fill = expression(paste(italic("E. coli"), " Risk Categories")),
       title = "R2 - March 2024"
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))



```


```{r Microbiological Contamination -- Follow-up r3}


#Removing NA result
idexx_r3 <- idexx_r3%>%
  filter(is.na(ec_mpn) == FALSE)%>%
  filter(sample_type != "Blank")%>% #Removing blanks
  filter(sample_type != "Solar") #Removing solar water samples

# Calculate descriptive statistics by village
village_stats_r3 <- village_stats(idexx_r3)

tc_stats_r3 <- tc_stats(idexx_r3)


all_stats_r3 <- all_stats(idexx_r3)


#Creating risk level stats for WHO Risk plot
risk_stats_r3 <- risk_stats(idexx_r3)

# Print the table
# kbl(village_stats_r3)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("r3 - Water Quality Test Results " = 7)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")
# 
# kbl(tc_stats_r3)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("r3 - Water Quality Test Results " = 11)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")
# 
# 
# kbl(all_stats_r3)%>%
#   kable_styling(bootstrap_options = "striped", full_width = TRUE) %>%
#   add_header_above(c("r3 - Water Quality Test Results " = 6)) %>%
#   row_spec(0, bold = TRUE, color = "black", background = "white") %>%
#   column_spec(1, bold = TRUE) %>%
#   column_spec(2, width = "75px")
# 
# 




#Plotting treatment/control stats on a bar plot
p_ec_r3 <- ggplot(data = tc_stats_r3) + 
  geom_col(aes(x = sample_type, y = `% Positive for E. coli`, fill = assignment), position = "dodge") +
  geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                    fill = assignment), position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "R3 - April 2024"
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_r3 <- ggplot(data = tc_stats_r3) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "R3 - April 2024"
       #title = expression(paste(" r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_r3 + p_ec_r3

#Fisher's Exact Test for differences between control and treatment
idexx_r3_stored <- idexx_r3%>%
  filter(sample_type == "Stored")

idexx_r3_tap <- idexx_r3%>%
  filter(sample_type == "Tap")

stored_cf <- fisher.test(x = idexx_r3_stored$assignment, y=idexx_r3_stored$cf_pa)

stored_ec <- fisher.test(x = idexx_r3_stored$assignment, y=idexx_r3_stored$ec_pa)

tap_cf <- fisher.test(x = idexx_r3_tap$assignment, y=idexx_r3_tap$cf_pa)

tap_ec <- fisher.test(x = idexx_r3_tap$assignment, y=idexx_r3_tap$ec_pa)

idexx_r3_signif <- data.frame(stored_cf$p.value, stored_ec$p.value, tap_cf$p.value, tap_ec$p.value)



#Making WHO risk plot
p_ec_risk_r3 <- ggplot(data = risk_stats_r3) + 
  geom_bar(aes(x = assignment, y = `E. coli Risk Levels %`, fill = ec_risk), position = "stack", stat = "identity") +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Assignment", 
       y = expression(paste("% for each risk category")),
       fill = expression(paste(italic("E. coli"), " Risk Categories")),
       title = "r3 - March 2024"
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))



```


### Pooled IDEXX Results


```{r Pooled IDEXX Results}

#Selecting only for follow-up survey data
idexx_fu <- idexx_tab%>%
  filter(pooled_round == "FU")

#Calculating key desc stats -- pooled rounds and baseline
tc_stats_pooled <- pooled_stats(idexx_fu)

tc_stats_bl <- pooled_stats(idexx)



#Creating figure of baseline IDEXX results

#Plotting treatment/control stats on a bar plot
p_ec_bl <- ggplot(data = tc_stats_bl) + 
  geom_col(aes(x = sample_type, y = `% Positive for E. coli`, fill = assignment), position = "dodge") +
  geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                    fill = assignment), position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_bl <- ggplot(data = tc_stats_bl) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "",
       caption = ""
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

#Patchwork package addition
p_bl <- 
  p_cf_bl + p_ec_bl +
  plot_annotation(
  title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 160)")),
  caption = "Stored and tap water samples were collected during the baseline survey round in October 2023."
)

p_bl





#Creating figure of pooled IDEXX results

#Plotting treatment/control stats on a bar plot
p_ec_pooled <- ggplot(data = tc_stats_pooled) + 
  geom_col(aes(x = sample_type, y = `% Positive for E. coli`, fill = assignment), position = "dodge") +
  geom_errorbar(aes(x = sample_type, ymin = `Lower CI - EC`, ymax = `Upper CI - EC`,
                    fill = assignment), position = position_dodge(width = 0.9),
                width = 0.25) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       fill = "Assignment",
       title = "",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

p_cf_pooled <- ggplot(data = tc_stats_pooled) + 
  geom_col(aes(x = sample_type, y = `% Positive for Total Coliform`, fill = assignment), position = "dodge") +
    geom_errorbar(aes(x = sample_type, ymin = `Lower CI - TC`, ymax = `Upper CI - TC`,
                      fill = assignment), position = position_dodge(width = 0.9),
                 width = 0.25) +
  #geom_signif(comparisons = list(c("Control", "Treatment"), map_signif_level = TRUE))+
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Sample Type", 
       y = expression(paste("% positive for total coliform")),
       fill = "Assignment",
       title = "",
       caption = ""
       )+
  theme_bw() + 
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))

#Patchwork package addition
p_pooled <- 
  p_cf_pooled + p_ec_pooled +
  plot_annotation(
  title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water (N = 481)")),
  caption = "Stored and tap water samples were pooled across 3 monthly household surveys rounds across 20 villages in February, March, and April 2024."
)

p_pooled



#Comparing IDEXX results to average chlorine concentration
idexx_fu <- idexx_fu%>%
  mutate(fc_tap_pa_2 = case_when(fc_tap_avg >= 0.2 ~ ">= 0.2 mg/L",
                                  fc_tap_avg < 0.2 ~ "< 0.2 mg/L"))%>%
  mutate(fc_stored_pa_2 = case_when(fc_stored_avg >= 0.2 ~ ">= 0.2 mg/L",
                                  fc_stored_avg < 0.2 ~ "< 0.2 mg/L"))
  

tap_stats_pooled <- idexx_fu%>%
  filter(sample_type == "Tap")%>%
    group_by(fc_tap_pa_2) %>%
    summarise(
      "Number of Samples" = n(),
      "% Positive for Total Coliform" = round((sum(cf_pa == "Presence") / n()) * 100, 1),
      "% Positive for E. coli" = round((sum(ec_pa == "Presence") / n()) * 100, 1),
      "% Tap Samples with Free Chlorine > 0.2 mg/L" = 
        round((sum(fc_tap_pa_2 == "Presence") / n()) * 100, 1),
      "% Stored Samples with Free Chlorine > 0.2 mg/L" = 
        round((sum(fc_stored_pa_2 == "Presence") / n()) * 100, 1)
      )

#Making plot to display chlorine results vs IDEXX results

p_tap_pooled <- ggplot(data = tap_stats_pooled) + 
  geom_col(aes(x = fc_tap_pa_2, y = `% Positive for E. coli`), position = "dodge") +
   geom_text(aes(x = fc_tap_pa_2, y = `% Positive for E. coli`,
                label = paste0(round(`% Positive for E. coli`, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Free Chlorine Concentration (mg/L)", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       title = "Tap Water",
       caption = ""
       #title = expression(paste(italic("E. coli"), " r3 - Presence in Tap and Stored Drinking Water in Odisha (N = 166)"))
       )+
  theme_bw()



stored_stats_pooled <- idexx_fu%>%
  filter(sample_type == "Stored")%>%
    group_by(fc_stored_pa_2) %>%
    summarise(
      "Number of Samples" = n(),
      "% Positive for Total Coliform" = round((sum(cf_pa == "Presence") / n()) * 100, 1),
      "% Positive for E. coli" = round((sum(ec_pa == "Presence") / n()) * 100, 1),
      "% Tap Samples with Free Chlorine > 0.2 mg/L" = 
        round((sum(fc_tap_pa_2 == "Presence") / n()) * 100, 1),
      "% Stored Samples with Free Chlorine > 0.2 mg/L" = 
        round((sum(fc_stored_pa_2 == "Presence") / n()) * 100, 1)
      )

#Making plot to display chlorine results vs IDEXX results

p_stored_pooled <- ggplot(data = stored_stats_pooled) + 
  geom_col(aes(x = fc_stored_pa_2, y = `% Positive for E. coli`), position = "dodge") +
  geom_text(aes(x = fc_stored_pa_2, y = `% Positive for E. coli`,
                label = paste0(round(`% Positive for E. coli`, 1), "%")),
            position = position_dodge(width = 0.9), vjust = -0.5) +
  scale_y_continuous(
                     limits = c(0, 100),
                     expand = c(0,0))+
  labs(x = "Free Chlorine Concentration (mg/L)", 
       y = expression(paste("% positive for ",italic("E. coli"))),
       title = "Stored Water",
       caption = ""
       )+
  theme_bw()


#Patchwork package addition
p_pooled <- 
  p_tap_pooled + p_stored_pooled +
  plot_annotation(
  title = expression(paste("Presence of Total Coliform and ", italic("E. coli"), " in Household Drinking Water vs Chlorine Concentration (N = 481)")),
  caption = "Stored and tap water samples were pooled across 3 monthly household surveys rounds across 20 villages in February, March, and April 2024."
)

p_pooled



```



## Regression Results Table -- Household Surveys

```{r Regression Results -- WASH variables, results='asis', output.dir = "C:/Users/jerem/Dropbox/Apps/Overleaf/India ILC Pilot- analysis"}



#Summarizing EL data and running regression models ----

#Selecting outcome variables
binary_vars <- c("prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary",
                 "tap_trust_binary", "tap_taste_binary", "tap_future_binary",
                 "fc_tap_binary", "fc_stored_binary")



#GT method
#Summarizing desc stats for each variable
#reset_gtsummary_theme()

desc_stats <- all_rounds%>%
  dplyr::select("assignment","data_round","prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary","tap_trust_binary", "tap_taste_binary", "tap_future_binary","fc_tap_binary", "fc_stored_binary")%>%
  tbl_strata(
    strata = data_round,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("prim_source_jjm", "sec_source", "jjm_drinking",
                             "water_treat_binary", "tap_trust_binary", "tap_taste_binary",
                             "tap_future_binary","fc_tap_binary",
                             "fc_stored_binary") ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(prim_source_jjm ~ "Government-provided tap as primary source",
                                 sec_source ~ "Use of a secondary source",
                                 jjm_drinking ~ "Use of government-provided taps for drinking",
                                 water_treat_binary ~ "Water treatment used",
                                 tap_trust_binary ~ "Trust in safety of taps",
                                 tap_taste_binary ~ "Satisfaction with taste from taps",
                                 tap_future_binary ~ "Likelihood of using taps in future",
                                 fc_tap_binary ~ "Presence of free chlorine in taps (>0.1 mg/L)",
                                 fc_stored_binary ~ "Presence of free chlorine in stored water (>0.1 mg/L)"
                                 )
                    )%>%
     modify_footnote(all_stat_cols() ~ "Mean (SD)"),
    .header = "**{strata}**"
  )%>%
  modify_footnote(update =  ~ "Mean (SD); BL - Oct 2023, R1 - February 2024, R2 - March 2024, R3 - April 2024")

desc_stats <- as_gt(desc_stats)%>%
  tab_options(table.font.size = 11)

#desc_stats


#Running regression models for each variable in the dataset

#Variables
outcome_vars <- c("prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary", "tap_trust_binary", "tap_taste_binary", "tap_future_binary")

#Running all models
#Logistic regression
all_models <- lapply(outcome_vars, 
                     function(var){ #This functions "subsets" the ilc_glm function
                       ilc_glm(data = bl_tab, var)
                     }
                       )
#linear regression
all_models <- lapply(outcome_vars, 
                     function(var){ #This functions "subsets" the ilc_glm function
                       ilc_lm(data = bl_tab, var)
                     }
                       )

#Assigning names to models
names(all_models) <- outcome_vars

#Making regression table output
ilc_model_table(all_models)


```


## Regression Results Table -- Microbiological Contamination

```{r Regression Results - Microbio contamination}

#Selecting followup survey data only, dropping baseline
 idexx_fu <- idexx_tab%>%
   filter(pooled_round == "FU")




#checking michelle's code for cases of IDEXX tests that do not match ---------
idexx_check <- idexx_mc%>%
  filter(!(unique_id %in% unique(idexx_fu$unique_id)))
#One ID which does match. In Michelle's data it's 1234567, which is not a real ID
#Michelle's data doesn't include sample IDs unfortunately...
idexx_check <- idexx_fu%>%
  filter(!(unique_id %in% unique(idexx_mc$unique_id)))
#No unique household IDs in my data that are not in Michelle's data
#My data has 245 stored water samples and 241 tap samples. There are 4 more stored samples than in Michelle's data. The tap sample seem to align.

#Tables
table(idexx_mc$round)
table(idexx_fu$data_round)
#it looks like michelle has 81 households in R1 and R2. I have 83 in R1 and 80 in R2. R3 has the same
#Looks like 1 sample is Michelle's R2 shouldn't be there

#checking additional cases in R2
idexx_check <- idexx_mc%>%
  filter(village == 10101) #There are 5 households sampled in Nathma 10101 in R2. The 1234567 household doesn't exist and should be removed? Need to check



#Separating stored vs tap water tests ------
idexx_ids <- idexx_tab%>%
  dplyr::select(assignment, village, block, panchayat_village, data_round, sample_ID, bag_ID_tap, bag_ID_stored)

idexx_tab_tap <- idexx_tab%>%
  filter(sample_type == "Tap")%>%
  filter(pooled_round == "FU")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, data_round, pooled_round, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_tap = "cf_pa_binary")%>%
  rename(ec_pa_tap = "ec_pa_binary")%>%
  rename(cf_log_tap = "cf_log")%>%
  rename(ec_log_tap = "ec_log")

idexx_tab_stored <- idexx_tab%>%
  filter(sample_type == "Stored")%>%
  filter(pooled_round == "FU")%>%
  dplyr::select(sample_ID, assignment, village, block, panchayat_village, data_round, pooled_round, cf_pa_binary, ec_pa_binary, cf_log, ec_log)%>%
  rename(cf_pa_stored = "cf_pa_binary")%>%
  rename(ec_pa_stored = "ec_pa_binary")%>%
  rename(cf_log_stored = "cf_log")%>%
  rename(ec_log_stored = "ec_log")


#Pivoting wider
# idexx_tab <- idexx_tab%>%
#   dplyr::select(sample_ID, sample_type, assignment, data_round, pooled_round, cf_pa_binary, ec_pa_binary, cf_log, ec_log)
# 
# idexx_tab <- idexx_tab%>%
#   pivot_wider(names_from = sample_type, values_from = c("cf_pa_binary", "ec_pa_binary", "cf_log", "ec_log"))%>%
#   rename(cf_pa_tap = "cf_pa_binary_Tap")%>%
#   rename(ec_pa_tap = "ec_pa_binary_Tap")%>%
#   rename(cf_log_tap = "cf_log_Tap")%>%
#   rename(ec_log_tap = "ec_log_Tap")%>%
#   rename(cf_pa_stored = "cf_pa_binary_Stored")%>%
#   rename(ec_pa_stored = "ec_pa_binary_Stored")%>%
#   rename(cf_log_stored = "cf_log_Stored")%>%
#   rename(ec_log_stored = "ec_log_Stored")


#idexx_tab <- left_join(idexx_ids, idexx_tab_tap, by = c("sample_ID", "bag_ID_tap"))










#Summarizing desc stats --------------------------------------

#Tap water

desc_stats <- idexx_tab_tap%>%
  dplyr::select(assignment, pooled_round, cf_pa_tap, ec_pa_tap, cf_log_tap, ec_log_tap
                )%>%
  tbl_strata(
    strata = pooled_round,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("cf_pa_tap", "ec_pa_tap", "cf_log_tap",
                             "ec_log_tap") ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(cf_pa_tap ~ "Tap - Presence/Absence of Total Coliform",
                                 ec_pa_tap ~ "Tap - Presence/Absence of E. coli",
                                 cf_log_tap ~ "Tap - Mean Log10 of Total Coliform",
                                 ec_log_tap ~ "Tap - Mean Log10 of E. coli"
                                )
                    )%>%
     modify_footnote(all_stat_cols() ~ "Mean (SD)"),
    .header = "**{strata}**"
  )%>%
  modify_footnote(update =  ~ "Mean (SD); BL - Baseline, FU - Followup")

desc_stats_tap <- as_gt(desc_stats)%>%
  tab_options(table.font.size = 11)

#desc_stats_tap



#Stored water


desc_stats <- idexx_tab_stored%>%
  dplyr::select(assignment, pooled_round, cf_pa_stored, ec_pa_stored, cf_log_stored, ec_log_stored
                )%>%
  tbl_strata(
    strata = pooled_round,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(by = assignment, 
                    missing = "no",
                    type = c("cf_pa_stored", "ec_pa_stored", "cf_log_stored",
                             "ec_log_stored") ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}%"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(cf_pa_stored ~ "Stored - Presence/Absence of Total Coliform",
                                 ec_pa_stored ~ "Stored - Presence/Absence of E. coli",
                                 cf_log_stored ~ "Stored - Mean Log10 of Total Coliform",
                                 ec_log_stored ~ "Stored - Mean Log10 of E. coli"
                                )
                    )%>%
     modify_footnote(all_stat_cols() ~ "Mean (SD)"),
    .header = "**{strata}**"
  )%>%
  modify_footnote(update =  ~ "Mean (SD); BL - Baseline, FU - Followup")

desc_stats_stored <- as_gt(desc_stats)%>%
  tab_options(table.font.size = 11)

#desc_stats_stored



#Running regression model results --------------------------------------------


#Tap Water
#Variables
outcome_vars <- c("cf_pa_tap", "ec_pa_tap")#, "cf_log_tap", "ec_log_tap")

#Running all models
#Logistic regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = idexx_tab_tap, var)
                 }
                  )
#linear regression
# all_models <- lapply(outcome_vars, 
#                      function(var){ #This functions "subsets" the ilc_glm function
#                        ilc_lm(data = idexx_tab_tap, var)
#                      }
#                        )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
ilc_model_table(all_models)


#Stored Water
#Variables
outcome_vars <- c("cf_pa_stored", "ec_pa_stored")#, "cf_log_stored", "ec_log_stored")

#Running all models
#Logistic regression
all_models <- lapply(outcome_vars,
                   function(var){ #This functions "subsets" the ilc_glm function
                    ilc_glm(data = idexx_tab_stored, var)
                 }
                  )
#linear regression
# all_models <- lapply(outcome_vars, 
#                      function(var){ #This functions "subsets" the ilc_glm function
#                        ilc_lm(data = idexx_tab_stored, var)
#                      }
#                        )

#Assigning names to models
names(all_models) <- outcome_vars


#Formatting table output
ilc_model_table(all_models)
















```


## Regression Results Table -- Baseline and Endline

```{r Regression Results -- Endline, results='asis', output.dir = "C:/Users/jerem/Dropbox/Apps/Overleaf/India ILC Pilot- analysis"}

#Baseline Census------------------------------------------------------------
#Subsetting datasets with key variables

cen_tab <- cen%>%
  dplyr::select(assignment, unique_id, 
                village, block, panchayat_village,
                prim_source, prim_source_jjm, sec_source, jjm_drinking, water_treat_binary
                )%>%
  mutate(data_round = "BL")




#Summarizing BL census data and running regression models ----

#Selecting variables
outcome_vars <- c("prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary")


#GT method
#Summarizing desc stats for each variable
desc_stats <- cen_tab%>%
  dplyr::select("assignment", "prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary")%>%
  tbl_summary(
  by = assignment,
  statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} / {N} ({p}%)"),
  digits = all_continuous() ~ 2
)%>%
  add_p()



#Running all models
#Logistic regression
#all_models <- lapply(outcome_vars, 
 #                    function(var){ #This functions "subsets" the ilc_glm function
  #                     ilc_glm(data = el_tab, var)
   #                  }
    #                   )
#linear regression
all_models <- lapply(outcome_vars, 
                     function(var){ #This functions "subsets" the ilc_glm function
                       ilc_lm(data = cen_tab, var)
                     }
                       )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
#ilc_model_table(all_models) #Need to fix






#Endline Census-------------------------------------------------------------
#Subsetting datasets with key variables

el_tab <- el%>%
  dplyr::select(assignment, unique_id, 
                village, block, panchayat_village,
                prim_source, prim_source_jjm, sec_source, jjm_drinking, water_treat_binary
                )%>%
  mutate(data_round = "EL")




#Summarizing EL data and running regression models ----

#Selecting variables
outcome_vars <- c("prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary")


#GT method
#Summarizing desc stats for each variable
desc_stats <- el_tab%>%
  dplyr::select("assignment", "prim_source_jjm", "sec_source", "jjm_drinking", "water_treat_binary")%>%
  tbl_summary(
  by = assignment,
  statistic = list(all_continuous() ~ "{mean} ({sd})", all_categorical() ~ "{n} / {N} ({p}%)"),
  digits = all_continuous() ~ 2
)%>%
  add_p()



#Running all models
#Logistic regression
#all_models <- lapply(outcome_vars, 
 #                    function(var){ #This functions "subsets" the ilc_glm function
  #                     ilc_glm(data = el_tab, var)
   #                  }
    #                   )
#linear regression
all_models <- lapply(outcome_vars, 
                     function(var){ #This functions "subsets" the ilc_glm function
                       ilc_lm(data = el_tab, var)
                     }
                       )

#Assigning names to models
names(all_models) <- outcome_vars

#Formatting table output
ilc_model_table(all_models)






# Combined Desc Stats -------------------------------------------------------

#Selecting jjm variables
el_jjm <- el%>%
  dplyr::select(assignment, prim_source, water_sec_yn, jjm_drinking, tap_issues, tap_issues_type_1)%>%
  mutate(data_round = "Endline")

cen_jjm <- cen%>%
  dplyr::select(assignment, prim_source, water_sec_yn, jjm_drinking)%>%
  mutate(data_round = "Baseline")%>%
  mutate(tap_issues = NA)%>%
  mutate(tap_issues_type_1 = NA)
#Combining EL and BL datasets
total_jjm <- rbind(cen_jjm, el_jjm)



#Summarizing combined results in a table
tab <- total_jjm%>%
  tbl_strata(
    strata = data_round,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(by = assignment, 
                    missing = "no", 
                    #type = c() ~ "continuous",
                    statistic = list(
                      all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{p}% ({n})"),
                    digits = list(all_continuous() ~ 2, 
                                  all_categorical() ~ 0),
                    label = list(prim_source ~ "Primary Drinking Water Source",
                                 jjm_drinking ~ "Use Government-provided Tap for Drinking",
                                 water_sec_yn ~ "Used a Secondary Drinking Water Source in Last Month",
                                 tap_issues ~ "Issues with Government-provided Tap (2 weeks)",
                                 tap_issues_type_1 ~ "Reported Taste/Odor/Cooking Issue"
                                 )
                    )%>%
     modify_footnote(all_stat_cols() ~ "% (N); BL - Oct 2023, EL - May 2024"),#%>%
 # as_gt()%>%
  #tab_options(table.font.size = pct(50),
              #table_body.hlines.width = 
   #             table.width = pct(50)),
    .header = "**{strata}**"
  )

# Convert to gt object
gt_tab <- as_gt(tab)


```




## Example/test code

```{r old robust standard error code}

#Taken from WASHPaLS analysis


#

#AEL_sandwich <- adjusted%>%
 # vcovCL(cluster = AEL_glm$village.x)

#robust_adjusted <- coeftest(adjusted, vcov. = AEL_sandwich) -- Code formerly used to calculate std errors
#Important to note that the code below already exponentiates the coefficients and std errors


# std.err <- sqrt(diag(AEL_sandwich))
# std.err <- std.err[1:((length(std.err)-4))]
# robust_adjusted <- tibble("pr"= exp(coef(adjusted)), "Std. Error" = exp(std.err),
# "Pr(>|z|)" = 2 * pnorm(abs(coef(adjusted)/std.err), lower.tail=FALSE),
# "LL" = exp(coef(adjusted) - 1.96 * (std.err)),
# "UL" = exp(coef(adjusted) + 1.96 * (std.err)))
# 
# #Creating readable 95% CI based on LL and UL
# robust_adjusted <- tibble(robust_adjusted,
#                            CI = paste("[", as.character(round(robust_adjusted$LL, digits = 3)), ",", as.character(round(robust_adjusted$UL, digits = 3)), "]"))
# 
# 
# #Storing values to final results tibble
# adjusted_pr <- robust_adjusted$pr[1]
# adjusted_ci <- robust_adjusted$CI[1]
# adjusted_p <- robust_adjusted$`Pr(>|z|)`[1]
# 
# 
# 
# outcome_result <- tibble(outcome = outcome,
#                   unadjusted_or = unadjusted_pr,
#                   unadjusted_ci = unadjusted_ci,
#                   unadjusted_p = unadjusted_p,
#                   adjusted_or = adjusted_pr,
#                   adjusted_ci = adjusted_ci,
#                   adjusted_p = adjusted_p,
#                   n = n)
# 






#Stargazer Method ---- 
#Calculating desc stats
#stargazer(el_tab[binary_vars], type = "latex", title = "Descriptive Statistics", out = "Manuscript_endline.tex")


#Running all models
# all_models <- lapply(binary_vars, 
#                      function(var) {
#                        formula <- as.formula(paste(var, "~ assignment + block + panchayat_village"))
#                        glm(formula, data = el_tab, family = "binomial")
# })

#Creating tables
# stargazer(all_models, type = "latex", title = "Regression Results", 
#           dep.var.labels = binary_vars, 
#           covariate.labels = c("Treatment", "Block (fixed effects)", "Panchayat Village (fixed effects)"),
#           omit = c("block", "panchayat_village"),
#           omit.labels = c("Block fixed effects", "Panchayat Village fixed effects"),
#           align = TRUE, no.space = TRUE, out = "manuscript_regression_results.tex")

#Outputting to overleaf








#Test code ------------------------------------------------------------------


#GT method
#Summarizing desc stats for each variable
#reset_gtsummary_theme()

#assignment, pooled_round, cf_pa_binary, ec_pa_binary, cf_log, ec_log
# desc_stats <- idexx_tab%>%
#   dplyr::select(assignment, pooled_round, cf_pa_tap, ec_pa_tap, cf_log_tap, ec_log_tap,
#                 cf_pa_stored, ec_pa_stored, cf_log_stored, ec_log_stored)%>%
#   tbl_strata(
#     strata = pooled_round,
#     .tbl_fun =
#       ~ .x %>%
#         tbl_summary(by = assignment, 
#                     missing = "no",
#                     type = c("cf_pa_tap", "ec_pa_tap", "cf_log_tap", "ec_log_tap",
#                 "cf_pa_stored", "ec_pa_stored", "cf_log_stored", "ec_log_stored") ~ "continuous",
#                     statistic = list(
#                       all_continuous() ~ "{mean} ({sd})",
#                       all_categorical() ~ "{p}%"),
#                     digits = list(all_continuous() ~ 2, 
#                                   all_categorical() ~ 0),
#                     label = list(cf_pa_tap ~ "Tap - Presence/Absence of Total Coliform",
#                                  ec_pa_tap ~ "Tap - Presence/Absence of E. coli",
#                                  cf_log_tap ~ "Tap - Mean Log10 of Total Coliform",
#                                  ec_log_tap ~ "Tap - Mean Log10 of E. coli",
#                                  cf_pa_stored ~ "Stored - Presence/Absence of Total Coliform",
#                                  ec_pa_stored ~ "Stored - Presence/Absence of E. coli",
#                                  cf_log_stored ~ "Stored - Mean Log10 of Total Coliform",
#                                  ec_log_stored ~ "Stored - Mean Log10 of E. coli"
#                                  )
#                     )%>%
#      modify_footnote(all_stat_cols() ~ "Mean (SD)"),
#     .header = "**{strata}**"
#   )%>%
#   modify_footnote(update =  ~ "Mean (SD); BL - Oct 2023, R1 - February 2024, R2 - March 2024, R3 - April 2024")
# 
# desc_stats <- as_gt(desc_stats)%>%
#   tab_options(table.font.size = 11)
# 
# desc_stats
# 



```





## Stata Translation

```{r Akito Stata translation}
# 
# # Load necessary libraries
# library(dplyr)
# library(tidyr)
# library(ggplot2)
# library(broom)
# 
# # Function to generate descriptive tables
# generate_descriptive_tables <- function(data, output_path) {
#   # Number of child-bearing age women
#   child_bearing_age_women <- data %>%
#     filter(R_Cen_a6_hhmember_age_ >= 15 & R_Cen_a6_hhmember_age_ <= 49 & R_Cen_a4_hhmember_gender_ == 2) %>%
#     group_by(village) %>%
#     summarise(count_1 = sum(!is.na(R_Cen_a6_hhmember_age_)))
#   print(summary(child_bearing_age_women$count_1))
#   # Number of children
#   children <- data %>%
#     filter(R_Cen_a6_hhmember_age_ >= 0 & R_Cen_a6_hhmember_age_ <= 14) %>%
#     group_by(village) %>%
#     summarise(count_1 = sum(!is.na(R_Cen_a6_hhmember_age_)))
#   print(summary(children$count_1))
#   # Number of pregnant women on average
#   pregnant_women <- data %>%
#     filter(R_Cen_a23_wom_diarr_day_ != . | R_Cen_a23_wom_diarr_week_ != . | R_Cen_a23_wom_diarr_2week_ != .) %>%
#     group_by(village) %>%
#     summarise(count_1 = sum(!is.na(R_Cen_a23_wom_diarr_day_)),
#               count_2 = sum(R_Cen_a6_hhmember_age_ >= 15 & R_Cen_a6_hhmember_age_ <= 49 & R_Cen_a4_hhmember_gender_ == 2)) %>%
#     mutate(perc_preg_women = count_1 / 192.22)
#   print(summary(pregnant_women$perc_preg_women))
#   # Number of U5 children on average
#   U5_children <- data %>%
#     filter(R_Cen_a6_hhmember_age_ < 5) %>%
#     group_by(village) %>%
#     summarise(count_1 = sum(!is.na(R_Cen_a6_hhmember_age_)),
#               count_2 = sum(R_Cen_a6_hhmember_age_ >= 0 & R_Cen_a6_hhmember_age_ <= 14)) %>%
#     mutate(perc_U5child = count_1 / 192.22)
#   print(summary(U5_children$perc_U5child))
#   # Number and average pregnant women + children <5 years per village
#   pregnant_women_children <- data %>%
#     filter(R_Cen_a23_wom_diarr_day_ != . | R_Cen_a23_wom_diarr_week_ != . | R_Cen_a23_wom_diarr_2week_ != . | R_Cen_a6_hhmember_age_ < 5) %>%
#     group_by(village) %>%
#     summarise(count_1 = sum(!is.na(R_Cen_a23_wom_diarr_day_) | !is.na(R_Cen_a6_hhmember_age_ < 5)),
#               count_2 = sum((R_Cen_a6_hhmember_age_ >= 15 & R_Cen_a6_hhmember_age_ <= 49 & R_Cen_a4_hhmember_gender_ == 2) | (R_Cen_a6_hhmember_age_ >= 0 & R_Cen_a6_hhmember_age_ <= 14))) %>%
#     mutate(perc_total = count_1 / 192.22)
#   print(summary(pregnant_women_children$perc_total))
# }
# # Load data
# data <- read.csv(path_to_data.csv)
# # Generate descriptive tables
# generate_descriptive_tables(data, output_path)
# # Number of HHs with pregnant women and children <5 years per village
# hh_pregnant_children <- data %>%
#   mutate(count1 = 1) %>%
#   rowwise() %>%
#   mutate(C_total_pregnant = sum(c_across(starts_with(R_Cen_a7_pregnant)) == 1, na.rm = TRUE)) %>%
#   ungroup() %>%
#   mutate(count2 = ifelse(C_total_pregnant > 0, 1, 0),
#          count3 = ifelse(R_Cen_screen_u5child == 1, 1, 0),
#          count4 = ifelse(C_Screened == 1, 1, 0)) %>%
#   group_by(R_Cen_village_name) %>%
#   summarise(count1 = sum(count1, na.rm = TRUE),
#             count2 = sum(count2, na.rm = TRUE),
#             count3 = sum(count3, na.rm = TRUE),
#             count4 = sum(count4, na.rm = TRUE)) %>%
#   mutate(perc_hh_preg = count2 / count1,
#          perc_hh_U5 = count3 / count1,
#          perc_hh_screened = count4 / count1)
# print(summary(hh_pregnant_children))
# # JJM access and other main vars - distribution by categories
# jjm_access <- data %>%
#   filter(!village %in% c(50601, 30601)) %>%
#   group_by(village) %>%
#   summarise(across(starts_with("R_Cen_a18"), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))))
# print(jjm_access)
# # Water sources
# water_sources <- data %>%
#   filter(!village %in% c(50601, 30601)) %>%
#   group_by(village) %>%
#   summarise(across(starts_with(R_Cen_a12_ws_prim), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))),
#             across(starts_with(R_Cen_a13_ws_sec), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))))
# print(water_sources)
# # Number of water sources people have
# water_sources_people <- data %>%
#   filter(!village %in% c(50601, 30601)) %>%
#   mutate(count_secondary_sources = rowSums(select(., starts_with(R_Cen_a13_ws_sec)), na.rm = TRUE),
#          count_primary_sources = rowSums(select(., starts_with(R_Cen_a12_ws_prim)), na.rm = TRUE),
#          total_num_sources = count_secondary_sources + count_primary_sources)
# print(water_sources_people)
# # JJM uses
# jjm_uses <- data %>%
#   filter(!village %in% c(50601, 30601)) %>%
#   group_by(village) %>%
#   summarise(across(starts_with(C_Cen_a18_jjm), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))))
# print(jjm_uses)
# # Water treatment
# water_treatment <- data %>%
#   filter(!village %in% c(50601, 30601)) %>%
#   group_by(village) %>%
#   summarise(across(starts_with(R_Cen_a16_water_treat), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))),
#             across(starts_with(R_Cen_a17_water_treat_kids), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))))
# print(water_treatment)
# # Water treatment frequency
# water_treatment_freq <- data %>%
#   filter(!village %in% c(50601, 30601)) %>%
#   group_by(village) %>%
#   summarise(across(starts_with(R_Cen_a16_water_treat_freq), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))),
#             across(starts_with(R_Cen_a17_treat_kids_freq), list(mean = ~mean(.x, na.rm = TRUE), sd = ~sd(.x, na.rm = TRUE))))
# print(water_treatment_freq)



```



