
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, message = FALSE)
```

```{r}
packages <- 
  c(
    "fixest",
    "broom",
    "tidyverse",
    "modelsummary"
  )

pacman::p_load(packages, character.only = TRUE)

# Data -------------------------------------------------------------------------

outcomes <-
  c(
    # "Presence of Total Coliform at Taps"= "cf_pa_tap",
    # "Presence of E. coli at Taps"= "ec_pa_tap",
    # "Presence of Total Coliform in Stored Water"= "cf_pa_stored",
    # "Presence of E. coli in Stored Water"= "ec_pa_stored",
    "Taps as Primary Source" = "prim_source_jjm",
    "Use a Secondary Source" = "sec_source",
    "Drink Tap Water" = "jjm_drinking",
    "Treat Water" = "water_treat_binary",
    "Treat Water > 5 min" = "time_spent_treat_5",
    "Reported Water Taste/Smell Issue" = "tap_issues_taste"
    
  )


# analysis <-
#   read_rds(
#     file.path(
#       user_path(),
#       "analysis_data.rds"
#     )
#   ) %>%
#   mutate(
#     water_treat_binary_bl = 1,
#     tap_taste_binary_bl = 1
#   )

# fu_village <-
#   analysis %>%
#   group_by(village, block, panchayat_village, stratum, assignment) %>%
#   summarise(
#     across(
#       c(outcomes) %>% unname,
#       ~ sum(., na.rm = TRUE)
#     ),
#     across(
#       ends_with("_bl"),
#       ~ unique(.)
#     ),
#     N = n()
#   )

analysis <- analysis%>%
  mutate(
    tap_issues_taste_bl = 1
  )%>%
  rename(time_spent_treat_5_bl = treat_time_5min_bl)
  

el_village <-
  analysis %>%
  group_by(village, block, panchayat_village, stratum, assignment) %>%
  summarise(
    across(
      c(outcomes) %>% unname,
      ~ sum(., na.rm = TRUE)
    ),
    across(
      ends_with("_bl"),
      ~ unique(.)
    ),
    N = n()
  )%>%
  mutate(
    tap_issues_taste_bl = 1
  )%>%
  rename(time_spent_treat_5_bl = treat_time_5min_bl)

# Running regression models -----------------------------------------------------

# Individual level -------------------------------------------------------------

# ind <-
#   outcomes%>%
#   map(
#     ~ list(
#         paste(., "~ assignment | block + panchayat_village"),
#         paste(., "~ assignment | stratum"),
#         paste(., "~ assignment"),
#         paste(., "~ assignment +", paste0(., "_bl")) 
#     ) %>%
#       map(~ as.formula(.)) %>%
#       map(
#         ~ feglm(
#           .,
#           data = analysis,
#           family = poisson,
#           cluster = ~ village
#         )
#       )
#   )
# 

# Village level ----------------------------------------------------------------

vil <-
  outcomes %>%
  map(
    ~ list(
       # paste(., "~ assignment + offset(log(N)) | block + panchayat_village"),
       # paste(., "~ assignment + offset(log(N)) | stratum"),
       # paste(., "~ assignment + offset(log(N))"),
      paste(., "~ assignment + offset(log(N)) +", paste0(., "_bl"))
    ) %>%
      map(~ as.formula(.)) %>%
      map(
        ~ feglm(
          .,
          data = el_village,
          family = poisson,
          se = 'iid'
        )
      )
  )

# Table ------------------------------------------------------------------------
add_rows <-
  tribble(
    ~name, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7, ~m8,
    "Control: baseline level", "", "", "", "X", "", "", "", "X"
  )
```

# Variables with baseline values available

- Columns 1 to 4 are from regression at the individual-round level. Columns 5-8 are at the village level.
- Column 1 is the current manuscript specification
- Column 8 is our suggested specification 

```{r}
map2(
  ind %>% head(7), 
  vil %>% head(7),
  ~ c(.x, .y)
) %>%
   modelsummary(
      coef_rename = c("assignmentTreatment" = "Treatment"),
      coef_omit = "^(?!.*Treatment)",
      shape = "rcollapse",
      gof_omit = "IC|R2|RMSE",
      add_rows = add_rows
    )
```

# Variables with no baseline observation

- Columns 1 to 3 are from regression at the individual-round level. Columns 4-6 are at the village level.
- Column 1 is the current manuscript specification
- Column 6 is our suggested specification 

```{r}
map2(
  ind %>% tail(2) %>% map(. %>% head(3)), 
  vil %>% tail(2) %>% map(. %>% head(3)),
  ~ c(.x, .y)
) %>%
  modelsummary(
    coef_rename = c("assignmentTreatment" = "Treatment"),
    coef_omit = "^(?!.*Treatment)",
    shape = "rcollapse",
    gof_omit = "IC|R2|RMSE"
  )

```




```{r IDEXX analysis}

outcomes <-
  c(
    "Presence of Total Coliform at Taps"= "cf_pa_tap",
    "Presence of E. coli at Taps"= "ec_pa_tap",
    "Presence of Total Coliform in Stored Water"= "cf_pa_stored",
    "Presence of E. coli in Stored Water"= "ec_pa_stored"
    
  )


#Prepping village level data
idexx_village <-
  analysis_idexx %>%
  group_by(village, block, panchayat_village, stratum, assignment) %>%
  summarise(
    across(
      c(outcomes) %>% unname,
      ~ sum(., na.rm = TRUE)
    ),
    across(
      ends_with("_bl"),
      ~ unique(.)
    ),
    N = n()
  )


# Running regression models -----------------------------------------------------

# Individual level -------------------------------------------------------------

# ind <-
#   outcomes%>%
#   map(
#     ~ list(
#         paste(., "~ assignment | block + panchayat_village"),
#         paste(., "~ assignment | stratum"),
#         paste(., "~ assignment"),
#         paste(., "~ assignment +", paste0(., "_bl")) 
#     ) %>%
#       map(~ as.formula(.)) %>%
#       map(
#         ~ feglm(
#           .,
#           data = analysis_idexx,
#           family = poisson,
#           cluster = ~ village
#         )
#       )
#   )


# Village level ----------------------------------------------------------------

vil <-
  outcomes %>%
  map(
    ~ list(
       # paste(., "~ assignment + offset(log(N)) | block + panchayat_village"),
       # paste(., "~ assignment + offset(log(N)) | stratum"),
       # paste(., "~ assignment + offset(log(N))"),
      paste(., "~ assignment + offset(log(N)) +", paste0(., "_bl"))
    ) %>%
      map(~ as.formula(.)) %>%
      map(
        ~ feglm(
          .,
          data = idexx_village,
          family = poisson,
          se = 'iid'
        )
      )
  )

# Table ------------------------------------------------------------------------
# add_rows <-
#   tribble(
#     ~name, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7, ~m8,
#     "Control: baseline level", "", "", "", "X", "", "", "", "X"
#   )




```



```{r ABR analysis}

outcomes <-
  c(
    "Presence of E. coli at Taps"= "ec_pa_abr_tap",
    "Presence of E. coli in Stored Water"= "ec_pa_abr_stored"
    
  )


#Prepping village level data
abr_village <-
  analysis_abr %>%
  group_by(village, block, panchayat_village, stratum, assignment) %>%
  summarise(
    across(
      c(outcomes) %>% unname,
      ~ sum(., na.rm = TRUE)
    ),
    across(
      ends_with("_bl"),
      ~ unique(.)
    ),
    N = n()
  )


# Running regression models -----------------------------------------------------

# Individual level -------------------------------------------------------------

ind <-
  outcomes%>%
  map(
    ~ list(
        paste(., "~ assignment | block + panchayat_village"),
        paste(., "~ assignment | stratum"),
        paste(., "~ assignment"),
        paste(., "~ assignment +", paste0(., "_bl")) 
    ) %>%
      map(~ as.formula(.)) %>%
      map(
        ~ feglm(
          .,
          data = analysis_abr,
          family = poisson,
          cluster = ~ village
        )
      )
  )


# Village level ----------------------------------------------------------------

vil <-
  outcomes %>%
  map(
    ~ list(
       paste(., "~ assignment + offset(log(N)) | block + panchayat_village"),
       paste(., "~ assignment + offset(log(N)) | stratum"),
       paste(., "~ assignment + offset(log(N))"),
      paste(., "~ assignment + offset(log(N)) +", paste0(., "_bl"))
    ) %>%
      map(~ as.formula(.)) %>%
      map(
        ~ feglm(
          .,
          data = abr_village,
          family = poisson,
          se = 'iid'
        )
      )
  )

# Table ------------------------------------------------------------------------
add_rows <-
  tribble(
    ~name, ~m1, ~m2, ~m3, ~m4, ~m5, ~m6, ~m7, ~m8,
    "Control: baseline level", "", "", "", "X", "", "", "", "X"
  )




```
